---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
```{R}
library(sets)
library(moments)
```

Load labels and the data.
```{r}
temp <- as.matrix(read.csv("/Users/Luke/Desktop/github/TDA-MSRI-2018/persit_2000_fixed/REFERENCE-v3.csv", header = F))
##DONT FORGET TO DELETE THE FIRST COLUMN!!! Not done here because it is already gone. 
```
##Load persistence variables
Load the persistence diagram variables.
```{r}
directory <-"/Users/Luke/Desktop/github/TDA-MSRI-2018/persit_2000_fixed/"

load_persistence_variable <- function(directory, labels, n){
  return(as.matrix(read.csv(file = paste0(directory, temp[n], ".csv")), header = T)[,-1])
}

num_pers <- 2392
#For loop will generate persistence variables.

for(i in seq(num_pers)){
  print(i)
  assign(paste0("persistence", i), load_persistence_variable(directory, labels, i))
}
```

##Counting Dimensions
Unimportant helper function. Counts the number of zeros, ones and two dimensional features in the persistence diagrams, given whatever persistence diagram you want.
```{r}
Counting_Dimensions <- function(n){
  tempFrame <- data.frame("Dimension" = get(paste0("persistence", n))[,1], "Birth" = get(paste0("persistence", n))[,2], "Death" = get(paste0("persistence", n))[,3])  
  return(table(tempFrame$Dimension))
}
```
#Extract noise.
```{r}
good_pers_index <- c()
pers_bad_index0 <- c()
pers_bad_index1 <- c()
pers_bad_index2 <- c()
pers_bad_index12 <- c()

for(i in seq(num_pers)){
  if(!is.na(Counting_Dimensions(i)[1]) & !is.na(Counting_Dimensions(i)[2]) & !is.na(Counting_Dimensions(i)[3]) ){
    good_pers_index <- append(good_pers_index, i)
  }
}
for(i in seq(num_pers)){
  if(is.na(Counting_Dimensions(i)[1])){
    pers_bad_index0 <- append(pers_bad_index0, i)
  }
  if(is.na(Counting_Dimensions(i)[2]) &  is.na(Counting_Dimensions(i)[3])){ #Check for files with no 0 dimensional features
    pers_bad_index12 <- append(pers_bad_index12, i)
  }
  if(is.na(Counting_Dimensions(i)[2])){ #Check for files with no 1 dimensional features
    pers_bad_index1 <- append(pers_bad_index1, i)
  }
  if(is.na(Counting_Dimensions(i)[3]) ){ #Check for files with no 2 dimensional features
    pers_bad_index2 <- append(pers_bad_index2, i)
  }
}

bad_files_dim1 <- c()
bad_files_dim2 <- c()
bad_files_dim12 <- c()

for(i in pers_bad_index1){
  bad_files_dim1 <- append(bad_files_dim1, temp[i,2])
}

for(i in pers_bad_index2){
  bad_files_dim2 <- append(bad_files_dim2, temp[i, 2]) 
}

for(i in pers_bad_index12){
  bad_files_dim12 <- append(bad_files_dim12, temp[i,2])
}
```

```{r}
normal_files <- c()
for(i in good_pers_index){
  if(temp[i,2] == "N"){
    normal_files <- append(normal_files, i)
  }
}

af_files <- c()
for(i in good_pers_index){
  if(temp[i,2] == "A"){
    af_files <- append(af_files, i)
  }
}

r_files <- c()
for(i in good_pers_index){
  if(temp[i,2] == "~"){
    r_files <- append(r_files, i)
  }
}

o_files <- c() 
for(i in good_pers_index){
  if(temp[i,2] == "O"){
    o_files <- append(o_files, i) 
  } 
}
```
##Export the labels.
```{R}
labels <- c()
for(i in seq(num_pers)){
  labels <- append(labels, temp[i,1])
} 

classes <- c() 
for(i in seq(num_pers)){
  classes <- append(classes, temp[i,2])
}
```

#Save as CSVs. 
```{r}
a <- data.frame("N" = temp[which(classes == "N"), 1])
b <- data.frame("AF" = temp[which(classes == "A"), 1])
c <- data.frame("Rand" = temp[which(classes == "~"), 1])
d <- data.frame("O" = temp[which(classes == "O"), 1])

write.csv(a, file = "Normal_2392.csv")
write.csv(b, file = "AF_2392.csv") 
write.csv(c, file = "Rand_2392.csv")
write.csv(d, file = "O_2392.csv") 
```

##Compute_dim_births and Compute_dim_deaths
Unimportant helper function. 
```{r} 
compute_zeros_birth <- function(n,a){
  L <- c()
  for(i in seq(a)){
   L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
}
compute_zeros_death <- function(n,a){
  L <- c()
  for(i in seq(a)){
   L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
}
###############################  
compute_ones_birth <- function(n,a,b){
  L <- c()
  for(i in seq(from=a+1, to=a+b)){
   L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
}
compute_ones_death <- function(n,a,b){
  L <- c()
  for(i in seq(from=a+1, to=a+b)){
   L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
}
#################
compute_twos_birth <- function(n,a,b,c){
  L <- c()
  for(i in seq(from=a+b+1, to=a+b+c)){
  L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
} 
compute_twos_death <- function(n,a,b,c){ 
  L <- c()
  for(i in seq(from=a+b+1, to=a+b+c)){
  L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
} 
``` 

##Extract_dim_biths and Extract_dim_deaths
Extracts the zero, one and two dimensional birth and death features.
```{r}
Extract_Birth_Zeros <- function(n){ #n is desired dimension
    p <- c()
    a <- Counting_Dimensions(n)[1]
    #b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth variables.
    assign(paste0("pers_", n, "_zeros_birth"), compute_zeros_birth(n,a))
    p <- append(p, get(paste0("pers_", n, "_zeros_birth")))
    return(p)
}
Extract_Death_Zeros <- function(n){ #n is desired dimension
    p <- c()
    a <- Counting_Dimensions(n)[1]
    #b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables
    assign(paste0("pers_", n, "_zeros_death"), compute_zeros_death(n,a))
    p <- append(p, get(paste0("pers_", n, "_zeros_death")))
    return(p)
    # k <- 0
    # assign(k, compute_zeros_death(n,a))
    # return(k)
}
Extract_Birth_Ones <- function(n){ #n is desired dimension
    p<- c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables.
    assign(paste0("pers_", n, "_ones_birth"), compute_ones_birth(n,a,b)) 
    p <- append(p, get(paste0("pers_", n, "_ones_birth")))
    return(p)
}
Extract_Death_Ones <- function(n){ #n is desired dimension
    p<- c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables.
    assign(paste0("pers_", n, "_ones_death"), compute_ones_death(n,a,b)) 
    p <- append(p, get(paste0("pers_", n, "_ones_death")))
    return(p)
}
Extract_Birth_Twos <- function(n){ #n is desired dimension
    p<-c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    c <- Counting_Dimensions(n)[3]
    
    #Assigns birth variables.
    assign(paste0("pers_", n, "_twos_birth"), compute_twos_birth(n,a,b,c)) 
    p <- append(p, get(paste0("pers_", n, "_twos_birth")))
    return(p)    
}
Extract_Death_Twos <- function(n){ #n is desired dimension
    p<-c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables. 
    assign(paste0("pers_", n, "_twos_death"), compute_twos_death(n,a,b,c)) 
    p <- append(p, get(paste0("pers_", n, "_twos_death")))
    return(p)    
}
```

##Store_birth_dim and Store_death_dim
Stores the zero, one and two dimensional birth and death features of each persistence diagram in your global environment. You will have many, many variables in your environment.
```{r}
# #Stores pers_zeros_births
# for(i in good_pers_index){
#    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
# }
# #Stores pers_zeros_deaths
# for(i in good_pers_index){
#    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
# }
# #Stores pers_ones_births
# for(i in good_pers_index){
#    assign(paste0("pers_", i, "_ones_birth"), Extract_Birth_Ones(i),envir=.GlobalEnv)
# }
# #Stores pers_ones_deaths
# for(i in good_pers_index){
#    assign(paste0("pers_", i, "_ones_death"), Extract_Death_Ones(i),envir=.GlobalEnv)
# }
# #Stores pers_twos_births
# for(i in good_pers_index){
#    assign(paste0("pers_", i, "_twos_birth"), Extract_Birth_Twos(i),envir=.GlobalEnv)
# }
# #Stores pers_twos_deaths
# for(i in good_pers_index){ 
#    assign(paste0("pers_", i, "_twos_death"), Extract_Death_Twos(i),envir=.GlobalEnv)
# } 
# 
# #Stores dumb motherfucking ones 
# for(i in pers_bad_index2){
#   assign(paste0("pers_", i, "_ones_birth"), Extract_Birth_Ones(i),envir=.GlobalEnv)
# }
# 
# for(i in pers_bad_index2){
#   assign(paste0("pers_", i, "_ones_death"), Extract_Death_Ones(i),envir=.GlobalEnv)
# }
# 
# for(i in pers_bad_index2){
#     assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
# }
# 
# for(i in pers_bad_index2){
#     assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
# }
#####Clean function#####
for(i in num_pers){
  if(i %in% good_pers_index){
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_birth"), Extract_Birth_Ones(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_death"), Extract_Death_Ones(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_birth"), Extract_Birth_Twos(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_death"), Extract_Death_Twos(i),envir=.GlobalEnv)
  }
  if(i %in% bad_pers_index1 & !(i %in%  bad_pers_index2)){#Has no 1 dimensional features, but 2 dimension features
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_birth"), Extract_Birth_Twos(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_death"), Extract_Death_Twos(i),envir=.GlobalEnv)
  }
  if(!(i %in% bad_pers_index1) & !(i %in% bad_pers_index)){#Has 1 dimensional features but no 2 dimensional features
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_birth"), Extract_Birth_Ones(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_death"), Extract_Death_Ones(i),envir=.GlobalEnv)    
  }
  if(i %in% bad_pers_index12){#Has no 1 or 2 dimensional features
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)    
  }
}


```

##Mean and SD of births across dimensions.
These functions below store the mean and standard deviation values across the birth values for dimensions one and two. We skip the births of dimension 0, since they're all 0s.
```{r}
mean_Births_Normal_dim_1 <- c()
mean_Births_Normal_dim_2 <- c()

sd_Births_Normal_dim_1 <- c()
sd_Births_Normal_dim_2 <- c()

mean_Births_AF_dim_1 <- c()
mean_Births_AF_dim_2 <- c()

sd_Births_AF_dim_1 <- c()
sd_Births_AF_dim_2 <- c()

mean_Births_Rand_dim_1 <- c()
mean_Births_Rand_dim_2 <- c()

sd_Births_Rand_dim_1 <- c()
sd_Births_Rand_dim_2 <- c()

mean_Births_O_dim_1 <- c()
mean_Births_O_dim_2 <- c()

sd_Births_O_dim_1 <- c()
sd_Births_O_dim_2 <- c()

for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    if(i %in% normal_files){
      mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

      mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 50)
    }
    if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
      sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
    }
    else{
      sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 80)
    }
}
    
    if(i %in% af_files){
  mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

  mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
    else{
      sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 50)
    }
  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 80)
  }
}

    if(i %in% r_files){
    mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 50)
  }

  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 80)
  }
}

    if(i %in% o_files){
    mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    mean_Births_O_dim_2 <- append(mean_Births_O_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 50)
  }

  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, 80)
  }
}
  }
  
  if(i %in% pers_bad_index2){
    print(i)
    if(temp[i,2] == "N"){
      mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))
      
      if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
        sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
      }
      else{
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1,80)
      }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, 100)
        sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 700)
    }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2, 300)
        sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 1000)
    }
      if(i %in% pers_bad_index12){ #10000
        mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, 100)
        mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2, 300)
        sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 700)
        sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 1000)
    }
  }

    if(temp[i,2] == "A"){
      mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 80)
    }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, 100)
        sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 700)
      }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2, 300)
        sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 1000)
      }
      if(i %in% pers_bad_index12){ #10000
        mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, 100)
        mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2, 300)
        sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 700)
        sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 1000)
    }
  }

    if(temp[i,2] == "~"){
      mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 80)
    } 
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, 100)
      sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 700)
  }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2, 300)
      sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, 100)
      mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2, 300)
      sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 700)
      sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 1000)
    }
    }
    
    if(temp[i,2] == "O"){
      mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))
      
    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 80)
    }      
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, 100)
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 700)
    }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, 100)
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      mean_Births_O_dim_2 <- append(mean_Births_O_dim_2, 300)
      sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, 100)
      mean_Births_O_dim_2 <- append(mean_Births_O_dim_2, 300)
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 700)
      sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, 1000)
    }
  }
  }
}
```

##Mean and SD of deaths across dimensions.
These functions below store the mean and standard deviation values across the death values for dimensions zero, one and two.
```{r}
mean_Deaths_Normal_dim_0 <- c()
mean_Deaths_Normal_dim_1 <- c()
mean_Deaths_Normal_dim_2 <- c() 

sd_Deaths_Normal_dim_0 <- c()
sd_Deaths_Normal_dim_1 <- c()
sd_Deaths_Normal_dim_2 <- c()

mean_Deaths_AF_dim_0 <- c()
mean_Deaths_AF_dim_1 <- c()
mean_Deaths_AF_dim_2 <- c()

sd_Deaths_AF_dim_0 <- c()
sd_Deaths_AF_dim_1 <- c()
sd_Deaths_AF_dim_2 <- c()

mean_Deaths_Rand_dim_0 <- c()
mean_Deaths_Rand_dim_1 <- c()
mean_Deaths_Rand_dim_2 <- c()

sd_Deaths_Rand_dim_0 <- c()
sd_Deaths_Rand_dim_1 <- c()
sd_Deaths_Rand_dim_2 <- c()

mean_Deaths_O_dim_0 <- c()
mean_Deaths_O_dim_1 <- c()
mean_Deaths_O_dim_2 <- c()

sd_Deaths_O_dim_0 <- c()
sd_Deaths_O_dim_1 <- c()
sd_Deaths_O_dim_2 <- c()

for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    if(i %in% normal_files){
  mean_Deaths_Normal_dim_0 <- append(mean_Deaths_Normal_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death")) != 1)){
    sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
    sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1,80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 30)
  }
}

    if(i %in% af_files){
  mean_Deaths_AF_dim_0 <- append(mean_Deaths_AF_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
    sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 30)
  }
}

    if(i %in% r_files){
  mean_Deaths_Rand_dim_0 <- append(mean_Deaths_Rand_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
  sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 30)
  }
}

    if(i %in% o_files){
  mean_Deaths_O_dim_0 <- append(mean_Deaths_O_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
  sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, 30)
  }
}
  }

  if(i %in% pers_bad_index2){ 
    if(temp[i,2] == "N"){
      mean_Deaths_Normal_dim_0 <- append(mean_Deaths_Normal_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
      
      if(length(get(paste0("pers_", i, "_zeros_death")) != 1)){
        sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      }
      else{
        sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, 50)
      }
      if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
        sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
      }
      else{
      sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1,80)
      }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, 100)
        sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, 700)
      }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        print(i)
        mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, 300)
        sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 1000)
    }
      if(i %in% pers_bad_index12){ #10000
        mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, 100)
        mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, 300)
        sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, 700)
        sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 1000)
    }
  }

    if(temp[i,2] == "A"){
      mean_Deaths_AF_dim_0 <- append(mean_Deaths_AF_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

    if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
      sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
    else{
      sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
      sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
    }
    else{
      sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 80)
    }
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, 100)
        sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 700)
      }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        print(i)
        mean_Deaths_AF_dim_2 <- append(mean_Deaths_AF_dim_2, 300)
        sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 1000)
      }
    if(i %in% pers_bad_index12){ #10000
        mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, 100)
        mean_Deaths_AF_dim_2 <- append(mean_Deaths_AF_dim_2, 300)
        sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 700)
        sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 1000)
    }
  }

    if(temp[i,2] == "~"){
      mean_Deaths_Rand_dim_0 <- append(mean_Deaths_Rand_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
      
    if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
      sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
    else{
      sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
      sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
    }
    else{
      sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 80)
    }      
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, 100)
      sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features 
      print(i)
      mean_Deaths_Rand_dim_2 <- append(mean_Deaths_Rand_dim_2, 300)
      sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, 100)
      mean_Deaths_Rand_dim_2 <- append(mean_Deaths_Rand_dim_2, 300)
      sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 700)
      sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 1000)
    }
  }
    
    if(temp[i,2] == "O"){
      mean_Deaths_O_dim_0 <- append(mean_Deaths_O_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

    if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){ 
      sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
    else{
      sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
      sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
    }
    else{
      sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 80)
    }      
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, 100)
      sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      print(i)
      mean_Deaths_O_dim_2 <- append(mean_Deaths_O_dim_2, 300)
      sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, 100)
      mean_Deaths_O_dim_2 <- append(mean_Deaths_O_dim_2, 300)
      sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 700)
      sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, 1000)
    }
  }
  } 
}
```

###HOLD THIS OBSOLETE CODE
```{r}
mean_Births_Normal_dim_1 <- c()
mean_Births_Normal_dim_2 <- c()

sd_Births_Normal_dim_1 <- c()
sd_Births_Normal_dim_2 <- c()

mean_Births_AF_dim_1 <- c()
mean_Births_AF_dim_2 <- c()

sd_Births_AF_dim_1 <- c()
sd_Births_AF_dim_2 <- c()

mean_Births_Rand_dim_1 <- c()
mean_Births_Rand_dim_2 <- c()

sd_Births_Rand_dim_1 <- c()
sd_Births_Rand_dim_2 <- c()

mean_Births_O_dim_1 <- c()
mean_Births_O_dim_2 <- c()

sd_Births_O_dim_1 <- c()
sd_Births_O_dim_2 <- c()

for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    if(i %in% normal_files){
      mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

      mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 50)
    }
    if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
      sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
    }
    else{
      sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 80)
    }
}
    
    if(i %in% af_files){
  mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

  mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
    else{
      sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 50)
    }
  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 80)
  }
}

    if(i %in% r_files){
    mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 50)
  }

  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 80)
  }
}

    if(i %in% o_files){
    mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    mean_Births_O_dim_2 <- append(mean_Births_O_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 50)
  }

  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, 80)
  }
}
  }
  
  if(i %in% pers_bad_index2){
    print(i)
    if(temp[i,2] == "N"){
      mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))
      
      if(length(get(paste0("pers_", i, "_zeros_birth")) != 1)){
        sd_Births_Normal_dim_0 <- append(sd_Births_Normal_dim_0, sd(get(paste0("pers_", i, "_zeros_birth"))[1:(length(get(paste0("pers_", i, "_zeros_birth")))-1)]))
      }
      else{
        sd_Births_Normal_dim_0 <- append(sd_Births_Normal_dim_0, 50)
      }
      if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
        sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
      }
      else{
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1,80)
      }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, 100)
        sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 700)
    }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2, 300)
        sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 1000)
    }
      if(i %in% pers_bad_index12){ #10000
        mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, 100)
        mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2, 300)
        sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 700)
        sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 1000)
    }
  }

    if(temp[i,2] == "A"){
      mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    if(length(get(paste0("pers_", i, "_zeros_birth"))) != 1){
      sd_Births_AF_dim_0 <- append(sd_Births_AF_dim_0, sd(get(paste0("pers_", i, "_zeros_birth"))[1:(length(get(paste0("pers_", i, "_zeros_birth")))-1)]))
    }
    else{
      sd_Births_AF_dim_0 <- append(sd_Births_AF_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 80)
    }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, 100)
        sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 700)
      }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2, 300)
        sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 1000)
      }
      if(i %in% pers_bad_index12){ #10000
        mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, 100)
        mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2, 300)
        sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 700)
        sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 1000)
    }
  }

    if(temp[i,2] == "~"){
      mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    if(length(get(paste0("pers_", i, "_zeros_birth"))) != 1){
      sd_Births_Rand_dim_0 <- append(sd_Births_Rand_dim_0, sd(get(paste0("pers_", i, "_zeros_birth"))[1:(length(get(paste0("pers_", i, "_zeros_birth")))-1)]))
    }
    else{
      sd_Births_Rand_dim_0 <- append(sd_Births_Rand_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 80)
    } 
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, 100)
      sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 700)
  }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2, 300)
      sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, 100)
      mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2, 300)
      sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 700)
      sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 1000)
    }
    }
    
    if(temp[i,2] == "O"){
      mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    if(length(get(paste0("pers_", i, "_zeros_birth"))) != 1){
      sd_Births_O_dim_0 <- append(sd_Births_O_dim_0, sd(get(paste0("pers_", i, "_zeros_birth"))[1:(length(get(paste0("pers_", i, "_zeros_birth")))-1)]))
    }
    else{
      sd_Births_O_dim_0 <- append(sd_Births_O_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 80)
    }      
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, 100)
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 700)
    }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, 100)
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      mean_Births_O_dim_2 <- append(mean_Births_O_dim_2, 300)
      sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, 100)
      mean_Births_O_dim_2 <- append(mean_Births_O_dim_2, 300)
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 700)
      sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, 1000)
    }
  }
  }
}
```
##Deaths
```{r}
mean_Deaths_Normal_dim_0 <- c()
mean_Deaths_Normal_dim_1 <- c()
mean_Deaths_Normal_dim_2 <- c()
 
sd_Deaths_Normal_dim_0 <- c()
sd_Deaths_Normal_dim_1 <- c()
sd_Deaths_Normal_dim_2 <- c()

mean_Deaths_AF_dim_0 <- c()
mean_Deaths_AF_dim_1 <- c()
mean_Deaths_AF_dim_2 <- c()

sd_Deaths_AF_dim_0 <- c()
sd_Deaths_AF_dim_1 <- c()
sd_Deaths_AF_dim_2 <- c()

mean_Deaths_Rand_dim_0 <- c()
mean_Deaths_Rand_dim_1 <- c()
mean_Deaths_Rand_dim_2 <- c()

sd_Deaths_Rand_dim_0 <- c()
sd_Deaths_Rand_dim_1 <- c()
sd_Deaths_Rand_dim_2 <- c()

mean_Deaths_O_dim_0 <- c()
mean_Deaths_O_dim_1 <- c()
mean_Deaths_O_dim_2 <- c()

sd_Deaths_O_dim_0 <- c()
sd_Deaths_O_dim_1 <- c()
sd_Deaths_O_dim_2 <- c()

for(i in seq(num_pers)){
  # print(temp[i,2])
  # print(i %in% good_pers_index)
  if(i %in% good_pers_index){
    if(i %in% normal_files){
      print(i)
  mean_Deaths_Normal_dim_0 <- append(mean_Deaths_Normal_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death")) != 1)){
    sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
    sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1,80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 30)
  }
}

    if(i %in% af_files){
  mean_Deaths_AF_dim_0 <- append(mean_Deaths_AF_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_AF_dim_2 <- append(mean_Deaths_AF_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
    sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 30)
  }
}

    if(i %in% r_files){
  mean_Deaths_Rand_dim_0 <- append(mean_Deaths_Rand_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_Rand_dim_2 <- append(mean_Deaths_Rand_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  
  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
  sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 30)
  }
}

    if(i %in% o_files){
  mean_Deaths_O_dim_0 <- append(mean_Deaths_O_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_O_dim_2 <- append(mean_Deaths_O_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  
  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
  sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, 30)
  }
}
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      mean_Deaths_Normal_dim_0 <- append(mean_Deaths_Normal_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

      if(length(get(paste0("pers_", i, "_zeros_death")) != 1)){
        sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      }
      else{
        sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, 50)
      }
      if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
        sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
      }
      else{
      sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1,80)
      }

      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, 100)
        sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, 700)
      }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        print(i)
        mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, 300)
        sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 1000)
    }
      if(i %in% pers_bad_index12){ #10000
        mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, 100)
        mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, 300)
        sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, 700)
        sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 1000)
    }
  }

    if(temp[i,2] == "A"){
      mean_Deaths_AF_dim_0 <- append(mean_Deaths_AF_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

    if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
      sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
    else{
      sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
      sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
    }
    else{
      sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 80)
    }

    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, 100)
        sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 700)
      }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        print(i)
        mean_Deaths_AF_dim_2 <- append(mean_Deaths_AF_dim_2, 300)
        sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 1000)
      }
    if(i %in% pers_bad_index12){ #10000
        mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, 100)
        mean_Deaths_AF_dim_2 <- append(mean_Deaths_AF_dim_2, 300)
        sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 700)
        sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 1000)
    }
  }

    if(temp[i,2] == "~"){
      mean_Deaths_Rand_dim_0 <- append(mean_Deaths_Rand_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

    if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
      sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
    else{
      sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
      sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
    }
    else{
      sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 80)
    }

    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, 100)
      sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      print(i)
      mean_Deaths_Rand_dim_2 <- append(mean_Deaths_Rand_dim_2, 300)
      sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, 100)
      mean_Deaths_Rand_dim_2 <- append(mean_Deaths_Rand_dim_2, 300)
      sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 700)
      sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 1000)
    }
  }

    if(temp[i,2] == "O"){
      mean_Deaths_O_dim_0 <- append(mean_Deaths_O_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

    if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
      sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
    else{
      sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
      sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
    }
    else{
      sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 80)
    }

    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, 100)
      sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      print(i)
      mean_Deaths_O_dim_2 <- append(mean_Deaths_O_dim_2, 300)
      sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, 100)
      mean_Deaths_O_dim_2 <- append(mean_Deaths_O_dim_2, 300)
      sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 700)
      sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, 1000)
    }
  }
  }
}
```

```{r}
mean_Births_Normal_dim_1 <- c()
mean_Births_Normal_dim_2 <- c()

sd_Births_Normal_dim_1 <- c()
sd_Births_Normal_dim_2 <- c()

for(i in normal_files){
    mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 50)
    }
    if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
      sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
    }
    else{
      sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 80)
    }
}

mean_Births_AF_dim_1 <- c()
mean_Births_AF_dim_2 <- c()

sd_Births_AF_dim_1 <- c()
sd_Births_AF_dim_2 <- c()

  for(i in af_files){
  mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

  mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 50)
  }
  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 80)
  }
}

mean_Births_Rand_dim_1 <- c()
mean_Births_Rand_dim_2 <- c()

sd_Births_Rand_dim_1 <- c()
sd_Births_Rand_dim_2 <- c()

  for(i in r_files){
  mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

  mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 50)
  }

  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 80)
  }
}

mean_Births_O_dim_1 <- c()
mean_Births_O_dim_2 <- c()

sd_Births_O_dim_1 <- c()
sd_Births_O_dim_2 <- c()

  for(i in o_files){
  mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

  mean_Births_O_dim_2 <- append(mean_Births_O_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 50)
  }

  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, 80)
  }
}

  for(i in pers_bad_index2){
  if(temp[i,2] == "N"){
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, 100)
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 700)
    }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2, 300)
        sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 1000)
    }
      if(i %in% pers_bad_index12){ #10000
        mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, 100)
        mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2, 300)
        sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 700)
        sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 1000)
    }
  }

  if(temp[i,2] == "A"){
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, 100)
        sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 700)
      }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2, 300)
        sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 1000)
      }
    if(i %in% pers_bad_index12){ #10000
        mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, 100)
        mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2, 300)
        sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 700)
        sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 1000)
    }
  }

  if(temp[i,2] == "R"){
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, 100)
      sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 700)
  }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2, 300)
      sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, 100)
      mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2, 300)
      sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 700)
      sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 1000)
    }
  }
  if(temp[i,2] == "~"){
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, 100)
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      mean_Births_O_dim_2 <- append(mean_Births_O_dim_2, 300)
      sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, 100)
      mean_Births_O_dim_2 <- append(mean_Births_O_dim_2, 300)
      sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 700)
      sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, 1000)
    }
  }
}


```

```{r}
mean_Deaths_Normal_dim_0 <- c()
mean_Deaths_Normal_dim_1 <- c()
mean_Deaths_Normal_dim_2 <- c()

sd_Deaths_Normal_dim_0 <- c()
sd_Deaths_Normal_dim_1 <- c()
sd_Deaths_Normal_dim_2 <- c()

for(i in normal_files){
  mean_Deaths_Normal_dim_0 <- append(mean_Deaths_Normal_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_death")))) 
  mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death")) != 1)){
    sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
    sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1,80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 30)
  }
}

mean_Deaths_AF_dim_0 <- c()
mean_Deaths_AF_dim_1 <- c()
mean_Deaths_AF_dim_2 <- c()

sd_Deaths_AF_dim_0 <- c()
sd_Deaths_AF_dim_1 <- c()
sd_Deaths_AF_dim_2 <- c()

for(i in af_files){
  mean_Deaths_AF_dim_0 <- append(mean_Deaths_AF_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_AF_dim_2 <- append(mean_Deaths_AF_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
    sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 30)
  }
}

mean_Deaths_Rand_dim_0 <- c()
mean_Deaths_Rand_dim_1 <- c()
mean_Deaths_Rand_dim_2 <- c()

sd_Deaths_Rand_dim_0 <- c()
sd_Deaths_Rand_dim_1 <- c()
sd_Deaths_Rand_dim_2 <- c()

for(i in r_files){
  mean_Deaths_Rand_dim_0 <- append(mean_Deaths_Rand_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_Rand_dim_2 <- append(mean_Deaths_Rand_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
  sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 30)
  }
}

mean_Deaths_O_dim_0 <- c()
mean_Deaths_O_dim_1 <- c()
mean_Deaths_O_dim_2 <- c()

sd_Deaths_O_dim_0 <- c()
sd_Deaths_O_dim_1 <- c()
sd_Deaths_O_dim_2 <- c()

for(i in o_files){
  mean_Deaths_O_dim_0 <- append(mean_Deaths_O_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_O_dim_2 <- append(mean_Deaths_O_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
  sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, 30)
  }
}


for(i in pers_bad_index2){
  if(temp[i,2] == "N"){
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, 100)
      sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, 700)
    }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, 300)
        sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 1000)
    }
      if(i %in% pers_bad_index12){ #10000
        mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, 100)
        mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, 300)
        sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, 700)
        sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 1000)
    }
  }

  if(temp[i,2] == "A"){
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, 100)
        sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 700)
      }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        mean_Deaths_AF_dim_2 <- append(mean_Deaths_AF_dim_2, 300)
        sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 1000)
      }
    if(i %in% pers_bad_index12){ #10000
        mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, 100)
        mean_Deaths_AF_dim_2 <- append(mean_Deaths_AF_dim_2, 300)
        sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 700)
        sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 1000)
    }
  }

  if(temp[i,2] == "R"){
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, 100)
      sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 700)
  }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      mean_Deaths_Rand_dim_2 <- append(mean_Deaths_Rand_dim_2, 300)
      sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, 100)
      mean_Deaths_Rand_dim_2 <- append(mean_Deaths_Rand_dim_2, 300)
      sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 700)
      sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 1000)
    }
  }
  if(temp[i,2] == "~"){
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, 100)
      sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      mean_Deaths_O_dim_2 <- append(mean_Deaths_O_dim_2, 300)
      sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, 100)
      mean_Deaths_O_dim_2 <- append(mean_Deaths_O_dim_2, 300)
      sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 700)
      sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, 1000)
    }
  }
}
```

##Append data.
The data is appended in the order of normal, AF, and random.
```{r}
#dim0, births
#Append the means, standard deviations. 
total_means_births_dim0 <-seq(0,0,length.out=num_pers)

total_sd_births_dim0 <- seq(0,0,length.out=num_pers) 

#dim0, deaths
#Append the means, standard deviations
total_means_deaths_dim0 <- append(append(append(mean_Deaths_Normal_dim_0, mean_Deaths_AF_dim_0), mean_Deaths_Rand_dim_0), mean_Deaths_O_dim_0) 

total_sd_deaths_dim0 <- append(append(append(sd_Deaths_Normal_dim_0, sd_Deaths_AF_dim_0), sd_Deaths_Rand_dim_0), sd_Deaths_O_dim_0) 

###################################################################
 
#dim1, births
#Append the means, standard deviations. 
total_means_births_dim1 <- append(append(append(mean_Births_Normal_dim_1, mean_Births_AF_dim_1), mean_Births_Rand_dim_1), mean_Births_O_dim_1)

total_sd_births_dim1 <- append(append(append(sd_Births_Normal_dim_1, sd_Births_AF_dim_1), sd_Births_Rand_dim_1), sd_Births_O_dim_1)

#dim1, deaths
#Append the means, standard deviations
total_means_deaths_dim1 <- append(append(append(mean_Deaths_Normal_dim_1, mean_Deaths_AF_dim_1), mean_Deaths_Rand_dim_1), mean_Deaths_O_dim_1)

total_sd_deaths_dim1 <- append(append(append(sd_Deaths_Normal_dim_1, sd_Deaths_AF_dim_1), sd_Deaths_Rand_dim_1), sd_Deaths_O_dim_1)

###################################################################

#dim2, births
#Append the means, standard deviations. 
total_means_births_dim2 <- append(append(append(mean_Births_Normal_dim_2, mean_Births_AF_dim_2), mean_Births_Rand_dim_2), mean_Births_O_dim_2)

total_sd_births_dim2 <- append(append(append(sd_Births_Normal_dim_2, sd_Births_AF_dim_2), sd_Births_Rand_dim_2), sd_Births_O_dim_2)

#dim2, deaths
#Append the means, standard deviations 
total_means_deaths_dim2 <- append(append(append(mean_Deaths_Normal_dim_2, mean_Deaths_AF_dim_2), mean_Deaths_Rand_dim_2), mean_Deaths_O_dim_2)

total_sd_deaths_dim2 <- append(append(append(sd_Deaths_Normal_dim_2, sd_Deaths_AF_dim_2), sd_Deaths_Rand_dim_2), sd_Deaths_O_dim_2)

```
##The good mistake: Reappend and get yo fucking shit together 
```{r}
################################ dim 0 ################################  
total_means_births_dim0 <-seq(0,0,length.out=num_pers)
total_sd_births_dim0 <- seq(0,0,length.out=num_pers) 

total_means_deaths_dim0 <- c()
total_sd_deaths_dim0 <-c()

#Store the death 0 dimensional means.
for(i in seq(length(labels))){ #Organize the death means of 0 dimension.
  print(i)
  if(i %in% normal_files){
    total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_Normal_dim_0[i])
  }
  if(i %in% af_files){
    total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_AF_dim_0[i])
  }
  if(i %in% r_files){
    total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_Rand_dim_0[i])
  }
  if(i %in% o_files){
    total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_O_dim_0[i])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_Normal_dim_0[i])
    }
    if(temp[i,2] == "A"){
      total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_AF_dim_0[i])
    }
    if(temp[i,2] == "~"){
      total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_Rand_dim_0[i])
    }
    if(temp[i,2] == "O"){
      total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_O_dim_0[i])
    }
  }
}

#Store the death 0 dimensional sd.
for(i in seq(length(labels))){ #Organize the deaht sd of 0 dimension.
  print(i)
  if(i %in% normal_files){
    total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_Normal_dim_0[i])
  }
  if(i %in% af_files){
    total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_AF_dim_0[i])
  }
  if(i %in% r_files){
    total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_Rand_dim_0[i])
  }
  if(i %in% o_files){
    total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_O_dim_0[i])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_Normal_dim_0[i])
    }
    if(temp[i,2] == "A"){
      total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_AF_dim_0[i])
    }
    if(temp[i,2] == "~"){
      total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_Rand_dim_0[i])
    }
    if(temp[i,2] == "O"){
      total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_O_dim_0[i])
    }  
}
}

################################ dim 1 ################################ 
total_means_births_dim1 <- c()
total_sd_births_dim1 <- c()
total_means_deaths_dim1 <- c()
total_sd_deaths_dim1 <- c()

#Store the birth 1 dimensional means.
for(i in seq(length(labels))){
  if(i %in% normal_files){
    total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_Normal_dim_1[i])
  }
  if(i %in% af_files){
    total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_AF_dim_1[i])
  }
  if(i %in% r_files){
    total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_Rand_dim_1[i])
  }
  if(i %in% o_files){
    total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_O_dim_1[i])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_Normal_dim_1[i])
    }
    if(temp[i,2] == "A"){
      total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_AF_dim_1[i])
    }
    if(temp[i,2] == "~"){
      total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_Rand_dim_1[i])
    }
    if(temp[i,2] == "O"){
      total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_O_dim_1[i])
    }  
}
}

#Store the birth 1 dimensional sd.
for(i in seq(length(labels))){ 
  if(i %in% normal_files){
    total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_Normal_dim_1[i])
  }
  if(i %in% af_files){
    total_sd_births_dim1 <- append(total_sd_births_dim1, mean_Births_AF_dim_1[i])
  }
  if(i %in% r_files){
    total_sd_births_dim1 <- append(total_sd_births_dim1, mean_Births_Rand_dim_1[i])
  }
  if(i %in% o_files){
    total_sd_births_dim1 <- append(total_sd_births_dim1, mean_Births_O_dim_1[i])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_Normal_dim_1[i])
    }
    if(temp[i,2] == "A"){
      total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_AF_dim_1[i])
    }
    if(temp[i,2] == "~"){
      total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_Rand_dim_1[i])
    }
    if(temp[i,2] == "O"){
      total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_O_dim_1[i])
    }  
}
}

#Store the death 1 dimensional means.
for(i in seq(length(labels))){ 
  print(i)
  if(i %in% normal_files){
    total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_Normal_dim_1[i])
  }
  if(i %in% af_files){
    total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_AF_dim_1[i])
  }
  if(i %in% r_files){
    total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_Rand_dim_1[i])
  }
  if(i %in% o_files){
    total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_O_dim_1[i])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_Normal_dim_1[i])
    }
    if(temp[i,2] == "A"){
      total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_AF_dim_1[i])
    }
    if(temp[i,2] == "~"){
      total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_Rand_dim_1[i])
    }
    if(temp[i,2] == "O"){
      total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_O_dim_1[i])
    }  
}
  
}

#Store the birth 1 dimensional sd.
for(i in seq(length(labels))){ 
  if(i %in% normal_files){
    total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_Normal_dim_1[i])
  }
  if(i %in% af_files){
    total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_AF_dim_1[i])
  }
  if(i %in% r_files){
    total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_Rand_dim_1[i])
  }
  if(i %in% o_files){
    total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_O_dim_1[i])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_Normal_dim_1[i])
    }
    if(temp[i,2] == "A"){
      total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_AF_dim_1[i])
    }
    if(temp[i,2] == "~"){
      total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_Rand_dim_1[i])
    }
    if(temp[i,2] == "O"){
      total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_O_dim_1[i])
    }  
}
}

################################ dim 2 ################################ 
total_means_births_dim2 <- c()
total_sd_births_dim2 <- c()

total_means_deaths_dim2 <- c()
total_sd_deaths_dim2 <- c()

#Store the birth 2 dimensional means.
for(i in seq(length(labels))){
  if(i %in% normal_files){
    total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_Normal_dim_2[i])
  }
  if(i %in% af_files){
    total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_AF_dim_2[i]) 
  }
  if(i %in% r_files){
    total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_Rand_dim_2[i])
  }
  if(i %in% o_files){
    total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_O_dim_2[i])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_Normal_dim_2[i])
    }
    if(temp[i,2] == "A"){
      total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_AF_dim_2[i]) 
    }
    if(temp[i,2] == "~"){
      total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_Rand_dim_2[i])
    }
    if(temp[i,2] == "O"){
      total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_O_dim_2[i])
    }  
}
}

#Store the birth 2 dimesional sd.
for(i in seq(length(labels))){ 
  if(i %in% normal_files){
    total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_Normal_dim_2[i])
  }
  if(i %in% af_files){
    total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_AF_dim_2[i]) 
  }
  if(i %in% r_files){
    total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_Rand_dim_2[i])
  }
  if(i %in% o_files){
    total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_O_dim_2[i])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_Normal_dim_2[i])
    }
    if(temp[i,2] == "A"){
      total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_AF_dim_2[i]) 
    }
    if(temp[i,2] == "~"){
      total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_Rand_dim_2[i])
    }
    if(temp[i,2] == "O"){
      total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_O_dim_2[i])
    }  
}
}

#Store the death 2 dimensional means
for(i in seq(length(labels))){ 
  if(i %in% normal_files){
    total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_Normal_dim_2[i])
  }
  if(i %in% af_files){
    total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_AF_dim_2[i])
  }
  if(i %in% r_files){
    total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_Rand_dim_2[i])
  }
  if(i %in% o_files){
    total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_O_dim_2[i])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_Normal_dim_2[i])
    }
    if(temp[i,2] == "A"){
      total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_AF_dim_2[i])
    }
    if(temp[i,2] == "~"){
      total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_Rand_dim_2[i])
    }
    if(temp[i,2] == "O"){
      total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_O_dim_2[i])
    }  
}
}

#Store the death 2 dimensional sd.
for(i in seq(length(labels))){  
  if(i %in% normal_files){
    total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_Normal_dim_2[i])
  }
  if(i %in% af_files){
    total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_AF_dim_2[i])
  }
  if(i %in% r_files){
    total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_Rand_dim_2[i])
  }
  if(i %in% o_files){
    total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_O_dim_2[i])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_Normal_dim_2[i])
    }
    if(temp[i,2] == "A"){
      total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_AF_dim_2[i])
    }
    if(temp[i,2] == "~"){
      total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_Rand_dim_2[i])
    }
    if(temp[i,2] == "O"){
      total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_O_dim_2[i])
    }  
}
}
```
##HOLD
```{r}
# ################################ dim 0 ################################  
# total_means_births_dim0 <-seq(0,0,length.out=num_pers)
# total_sd_births_dim0 <- seq(0,0,length.out=num_pers) 
# 
# total_means_deaths_dim0 <- c()
# total_sd_deaths_dim0 <-c()
# 
# #Store the death 0 dimensional means.
# for(i in seq(length(labels))){ #Organize the death means of 0 dimension.
#   print(i)
#   if(temp[i,1] == temp[normal_files[i], 1]){
#     total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_Normal_dim_0[i])
#   }
#   if(i %in% af_files){
#     total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_AF_dim_0[i])
#   }
#   if(temp[i,1] == temp[r_files[i], 1]){
#     total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_Rand_dim_0[i])
#   }
#   if(temp[i,1] == temp[o_files[i], 1]){
#     total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_O_dim_0[i])
#   }
#   if(temp[i, 1] == temp[pers_bad_index2[i], 1]){
#     if(temp[i,2] == "N"){
#       total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_Normal_dim_0[i])
#     }
#     if(temp[i,2] == "A"){
#       total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_AF_dim_0[i])
#     }
#     if(temp[i,2] == "~"){
#       total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_Rand_dim_0[i])
#     }
#     if(temp[i,2] == "O"){
#       total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_O_dim_0[i])
#     }
#   }
# }
# 
# #Store the death 0 dimensional sd.
# for(i in seq(length(labels))){ #Organize the deaht sd of 0 dimension.
#   print(i)
#   if(temp[i,1] == temp[normal_files[i],1]){
#     total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_Normal_dim_0[i])
#   }
#   if(temp[i,1] == temp[af_files[i], 1]){
#     total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_AF_dim_0[i])
#   }
#   if(temp[i,1] == temp[r_files[i],1]){
#     total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_Rand_dim_0[i])
#   }
#   if(temp[i,1] == temp[o_files[i],1]){
#     total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_O_dim_0[i])
#   }
#   if(temp[i, 1] == temp[pers_bad_index2[i],1]){
#     if(temp[i,2] == "N"){
#       total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_Normal_dim_0[i])
#     }
#     if(temp[i,2] == "A"){
#       total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_AF_dim_0[i])
#     }
#     if(temp[i,2] == "~"){
#       total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_Rand_dim_0[i])
#     }
#     if(temp[i,2] == "O"){
#       total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_O_dim_0[i])
#     }  
# }
# }
# 
# ################################ dim 1 ################################ 
# total_means_births_dim1 <- c()
# total_sd_births_dim1 <- c()
# total_means_deaths_dim1 <- c()
# total_sd_deaths_dim1 <- c()
# 
# #Store the birth 1 dimensional means.
# for(i in seq(length(labels))){
#   if(temp[i,1] == temp[normal_files[i],1]){
#     total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_Normal_dim_1[i])
#   }
#   if(temp[i,1] == temp[af_files[i],1]){
#     total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_AF_dim_1[i])
#   }
#   if(temp[i,1] == temp[r_files[i],1]){
#     total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_Rand_dim_1[i])
#   }
#   if(temp[i,1] == temp[o_files[i],1]){
#     total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_O_dim_1[i])
#   }
#   if(temp[i, 1] == temp[pers_bad_index2[i],1]){
#     if(temp[i,2] == "N"){
#       total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_Normal_dim_1[i])
#     }
#     if(temp[i,2] == "A"){
#       total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_AF_dim_1[i])
#     }
#     if(temp[i,2] == "~"){
#       total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_Rand_dim_1[i])
#     }
#     if(temp[i,2] == "O"){
#       total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_O_dim_1[i])
#     }  
# }
# }
# 
# #Store the birth 1 dimensional sd.
# for(i in seq(length(labels))){ 
#   if(temp[i,1] == temp[normal_files[i],1]){
#     total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_Normal_dim_1[i])
#   }
#   if(temp[i,1] == temp[af_files[i],1]){
#     total_sd_births_dim1 <- append(total_sd_births_dim1, mean_Births_AF_dim_1[i])
#   }
#   if(temp[i,1] == temp[r_files[i],1]){
#     total_sd_births_dim1 <- append(total_sd_births_dim1, mean_Births_Rand_dim_1[i])
#   }
#   if(temp[i,1] == temp[o_files[i],1]){
#     total_sd_births_dim1 <- append(total_sd_births_dim1, mean_Births_O_dim_1[i])
#   }
#   if(temp[i, 1] == temp[pers_bad_index2[i],1]){
#     if(temp[i,2] == "N"){
#       total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_Normal_dim_1[i])
#     }
#     if(temp[i,2] == "A"){
#       total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_AF_dim_1[i])
#     }
#     if(temp[i,2] == "~"){
#       total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_Rand_dim_1[i])
#     }
#     if(temp[i,2] == "O"){
#       total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_O_dim_1[i])
#     }  
# }
# }
# 
# #Store the death 1 dimensional means.
# for(i in seq(length(labels))){ 
#   if(temp[i,1] == temp[normal_files[i],1]){
#     total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_Normal_dim_1[i])
#   }
#   if(temp[i,1] == temp[af_files[i],1]){
#     total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_AF_dim_1[i])
#   }
#   if(temp[i,1] == temp[r_files[i],1]){
#     total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Death_Rand_dim_1[i])
#   }
#   if(temp[i,1] == temp[o_files[i],1]){
#     total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_O_dim_1[i])
#   }
#   if(temp[i, 1] ==  temp[pers_bad_index2[i],1]){
#     if(temp[i,2] == "N"){
#       total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_Normal_dim_1[i])
#     }
#     if(temp[i,2] == "A"){
#       total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_AF_dim_1[i])
#     }
#     if(temp[i,2] == "~"){
#       total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Death_Rand_dim_1[i])
#     }
#     if(temp[i,2] == "O"){
#       total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_O_dim_1[i])
#     }  
# }
#   
# }
# 
# #Store the birth 1 dimensional sd.
# for(i in seq(length(labels))){ 
#   if(temp[i,1] == temp[normal_files[i],1]){
#     total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_Normal_dim_1[i])
#   }
#   if(temp[i,1] == temp[af_files[i],1]){
#     total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_AF_dim_1[i])
#   }
#   if(temp[i,1] == temp[r_files[i],1]){
#     total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_Rand_dim_1[i])
#   }
#   if(temp[i,1] == temp[o_files[i],1]){
#     total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_O_dim_1[i])
#   }
#   if(temp[i, 1] == temp[pers_bad_index2[i],1]){
#     if(temp[i,2] == "N"){
#       total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_Normal_dim_1[i])
#     }
#     if(temp[i,2] == "A"){
#       total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_AF_dim_1[i])
#     }
#     if(temp[i,2] == "~"){
#       total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_Rand_dim_1[i])
#     }
#     if(temp[i,2] == "O"){
#       total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_O_dim_1[i])
#     }  
# }
# }
# 
# ################################ dim 2 ################################ 
# total_means_births_dim2 <- c()
# total_means_deaths_dim2 <- c()
# 
# total_means_deaths_dim2 <- c()
# total_sd_deaths_dim2 <- c()
# #Store the birth 2 dimensional means.
# for(i in seq(length(labels))){
#   if(temp[i,1] == temp[normal_files[i],1]){
#     total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_Normal_dim_2[i])
#   }
#   if(temp[i,1] == temp[af_files[i],1]){
#     total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_AF_dim_2[i]) 
#   }
#   if(temp[i,1] ==  temp[r_files[i],1]){
#     total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_Rand_dim_2[i])
#   }
#   if(temp[i,1] == temp[o_files[i],1]){
#     total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_O_dim_2[i])
#   }
#   if(temp[i, 1] == temp[pers_bad_index2[i],1]){
#     if(temp[i,2] == "N"){
#       total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_Normal_dim_2[i])
#     }
#     if(temp[i,2] == "A"){
#       total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_AF_dim_2[i]) 
#     }
#     if(temp[i,2] == "~"){
#       total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_Rand_dim_2[i])
#     }
#     if(temp[i,2] == "O"){
#       total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_O_dim_2[i])
#     }  
# }
# }
# 
# #Store the birth 2 dimesional sd.
# for(i in seq(length(labels))){ 
#   if(temp[i,1] == temp[normal_files[i],1]){
#     total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_Normal_dim_2[i])
#   }
#   if(temp[i,1] == temp[af_files[i],1]){
#     total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_AF_dim_2[i]) 
#   }
#   if(temp[i,1] ==  temp[r_files[i],1]){
#     total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_Rand_dim_2[i])
#   }
#   if(temp[i,1] == temp[o_files[i],1]){
#     total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_O_dim_2[i])
#   }
#   if(temp[i, 1] == temp[pers_bad_index2[i],1]){
#     if(temp[i,2] == "N"){
#       total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_Normal_dim_2[i])
#     }
#     if(temp[i,2] == "A"){
#       total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_AF_dim_2[i]) 
#     }
#     if(temp[i,2] == "~"){
#       total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_Rand_dim_2[i])
#     }
#     if(temp[i,2] == "O"){
#       total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_O_dim_2[i])
#     }  
# }
# }
# 
# #Store the death 2 dimensional means
# for(i in seq(length(labels))){ 
#   if(temp[i,1] == temp[normal_files[i],1]){
#     total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_Normal_dim_2[i])
#   }
#   if(temp[i,1] == temp[af_files[i],1]){
#     total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_AF_dim_2[i])
#   }
#   if(temp[i,1] ==  temp[r_files[i],1]){
#     total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_Rand_dim_2[i])
#   }
#   if(temp[i,1] == temp[o_files[i],1]){
#     total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_O_dim_2[i])
#   }
#   if(temp[i, 1] == temp[pers_bad_index2[i],1]){
#     if(temp[i,2] == "N"){
#       total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_Normal_dim_2[i])
#     }
#     if(temp[i,2] == "A"){
#       total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_AF_dim_2[i])
#     }
#     if(temp[i,2] == "~"){
#       total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_Rand_dim_2[i])
#     }
#     if(temp[i,2] == "O"){
#       total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_O_dim_2[i])
#     }  
# }
# }
# 
# #Store the death 2 dimensional sd.
# for(i in seq(length(labels))){  
#   if(temp[i,1] == temp[normal_files[i],1]){
#     total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_Normal_dim_2[i])
#   }
#   if(temp[i,1] == temp[af_files[i],1]){
#     total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_AF_dim_2[i])
#   }
#   if(temp[i,1] ==  temp[r_files[i],1]){
#     total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_Rand_dim_2[i])
#   }
#   if(temp[i,1] == temp[o_files[i],1]){
#     total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_O_dim_2[i])
#   }
#   if(temp[i,1] == temp[pers_bad_index2[i],1]){
#     if(temp[i,2] == "N"){
#       total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_Normal_dim_2[i])
#     }
#     if(temp[i,2] == "A"){
#       total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_AF_dim_2[i])
#     }
#     if(temp[i,2] == "~"){
#       total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_Rand_dim_2[i])
#     }
#     if(temp[i,2] == "O"){
#       total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_O_dim_2[i])
#     }  
# }
# }
```

##Organize mean, sd data into dataframe
```{r}
export_dim0 <- data.frame("Means_dim0_birth" = total_means_births_dim0, "Means_dim0_death" = total_means_deaths_dim0, "sd_dim0_birth" = total_sd_births_dim0, "sd_dim0_death" = total_sd_deaths_dim0)

export_dim1 <- data.frame("Means_dim1_birth" = total_means_births_dim1, "Means_dim1_death" = total_means_deaths_dim1, "sd_dim1_birth" = total_sd_births_dim1, "sd_dim1_death" = total_sd_deaths_dim1)
 
export_dim2 <- data.frame("Means_dim2_birth" = total_means_births_dim2, "Means_dim2_death" = total_means_deaths_dim2, "sd_dim2_birth" = total_sd_births_dim2, "sd_dim2_death" = total_sd_deaths_dim2)
```

```{r}
write.csv(export_dim0, "Organized_Mean_sd_dimension_0.csv") 
write.csv(export_dim1, "Organized_Mean_sd_dimension_1.csv") 
write.csv(export_dim2, "Organized_Mean_sd_dimension_2.csv")

```

##Calculate sum of lifetimes
The lifetimes are summed across the dimensions per each persistence diagram.
```{r} 
#Lifetimes for d imension 0 
lifetimes_dim0 <- c()
for(i in seq(num_pers)){
  lifetime <- sum(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)])
  lifetimes_dim0 <- append(lifetimes_dim0, lifetime)
}

#Lifetimes for dimension 1.
lifetimes_dim1 <- c()
for(i in seq(num_pers)){
  lifetime <- sum(get(paste0("pers_", i, "_ones_death"))) - sum(get((paste0("pers_", i, "_ones_birth"))))
  lifetimes_dim1 <- append(lifetimes_dim1, lifetime)
}

#Lifetimes for dimension 2.
lifetimes_dim2 <- c()
for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    lifetime <- sum((get(paste0("pers_", i, "_twos_death")))) - sum(get((paste0("pers_", i, "_twos_birth"))))
    lifetimes_dim2 <- append(lifetimes_dim2, lifetime)
  }
  
  else{
    lifetime <- 400
    lifetimes_dim2 <- append(lifetimes_dim2, lifetime)
  }
}
```

##Oraganize lifetime data into a dataframe, export as CSV.
```{r} 
lifetimedata <- data.frame("Lifetime_dim0" = lifetimes_dim0, "Lifetime_dim1" = lifetimes_dim1, "Lifetime_dim2" = lifetimes_dim2)
write.csv(lifetimedata, file = "Lifetimes_dim_0_1_2.csv")
```

##Caclulate maximum hole lifetimes
Calculates the maximum lifetime of each feature across all dimensions per persistence diagram.
```{r} 
maxs_dim0 <- c()
for(i in seq(nump_pers)){
  hold_lifetimes <- c()
  print(i)
  for(j in seq(length(get(paste0("pers_", i, "_zeros_death"))))){
    hold_lifetimes <- append(hold_lifetimes, (get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
 
   maxs_dim0 <- append(maxs_dim0, max(hold_lifetimes))
} 

maxs_dim1 <- c()
for(i in seq(num_pers)){
  hold_lifetimes <- c()
  print(i) 
  for(j in seq(length(get(paste0("pers_", i, "_ones_death"))))){
    hold_lifetimes <- append(hold_lifetimes, (get(paste0("pers_", i, "_ones_death"))[j] - get(paste0("pers_", i, "_ones_birth"))))
    }
 
   maxs_dim1 <- append(maxs_dim1, max(hold_lifetimes))
}
maxs_dim2 <- c()
for(i in seq(num_pers)){
  hold_lifetimes <- c()
  print(i)
  for(j in seq(length(get(paste0("pers_", i, "_twos_death"))))){
    hold_lifetimes <- append(hold_lifetimes, (get(paste0("pers_", i, "_twos_death"))[j] - get(paste0("pers_", i, "_twos_birth"))))
    }
 
   maxs_dim2 <- append(maxs_dim2, max(hold_lifetimes))
}
```

##Convert to dataframe, export as CSV.
```{r}
max_lifetimes <- data.frame("Max_life_dim0" = maxs_dim0, "Max_life_dim1" = maxs_dim1, "Max_life_dim2" = maxs_dim2)
write.csv(max_lifetimes, file = "Maximum_lifetimes_all_dims.csv")
```

##Calculate the skewness for births, deaths
Calculates the skewness across the births for dimensions 1, 2 and deaths for dimensions 0,1,2 per persistence diagram.
```{r} 
###################################Births#########################################
skewness_births_dim0 <- seq(0,0, length.out = num_pers)

skewness_births_dim1 <- c()
for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    hold_pers <- get(paste0("pers_", i, "_ones_birth"))
    if(!(length(hold_pers) <= 1) ){
    skewness_births_dim1 <- append(skewness_births_dim1, skewness(hold_pers))
    }
    if(length(hold_pers)<= 1){
      skewness_births_dim1 <- append(skewness_births_dim1, 80)
    }
  }
  if(i %in% pers_bad_index2){
    skewness_births_dim1 <- append(skewness_births_dim1, 30)
  }
}

skewness_births_dim2 <- c()
for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    hold_pers <- get(paste0("pers_", i, "_twos_birth"))
    if( !(length(hold_pers) <= 1) ){
      skewness_births_dim2 <- append(skewness_births_dim2, skewness(hold_pers))
    }
    if(length(hold_pers) <= 1){
      skewness_births_dim2 <- append(skewness_births_dim2, 40)
    }
  }
  if(i %in% pers_bad_index2){
    skewness_births_dim2 <- append(skewness_births_dim2, 100)
  }
}  
###################################Deaths#########################################

skewness_deaths_dim0 <- c()
for(i in seq(num_pers)){
  hold_pers <- get(paste0("pers_", i, "_zeros_death"))
  if( !(length(hold_pers) <= 1) ){    
    skewness_deaths_dim0 <- append(skewness_deaths_dim0, skewness(hold_pers[1:(length(hold_pers)-1)]))
  }
}

skewness_deaths_dim1 <- c()
for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    hold_pers <- get(paste0("pers_", i, "_ones_death"))
    if( !(length(hold_pers) <= 1) ){    
      skewness_deaths_dim1 <- append(skewness_deaths_dim1, skewness(hold_pers))
    }
  }
  if(i %in% pers_bad_index2){
    skewness_deaths_dim1 <- append(skewness_deaths_dim1, 60)
  }
}
  
skewness_deaths_dim2 <- c()
for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    hold_pers <- get(paste0("pers_", i, "_twos_death"))
    if( !(length(hold_pers) <= 1) ){    
      skewness_deaths_dim2 <- append(skewness_deaths_dim2, skewness(hold_pers))
    }
    if( length(hold_pers) <= 1){
      skewness_deaths_dim2 <- append(skewness_deaths_dim2, 130)
    }
  }
    if(i %in% pers_bad_index2){
      print(i)
      skewness_deaths_dim2 <- append(skewness_deaths_dim2, 200)
  }
}
```

##Calculate the kurtosis for births, deaths
Calculates the kurtosis value across the births for dimension 1, 2 and deaths for dimensions 0, 1, 2 per persistence diagram.
```{r} 
#########################Births############################
kurtosis_births_dim0 <- seq(0, 0, length.out = seq(num_pers))

kurtosis_births_dim1 <- c()
for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    hold_pers <- get(paste0("pers_", i, "_ones_birth"))
    if(!(length(hold_pers) <= 1) ){
      kurtosis_births_dim1 <- append(kurtosis_births_dim1, kurtosis(hold_pers))
    }
    if(length(hold_pers) <= 1){
      kurtosis_births_dim1 <- append(kurtosis_births_dim1, 300)
    }
  }
  if(i %in% pers_bad_index2){
    kurtosis_births_dim1 <- append(kurtosis_births_dim1, 500)
  }
}

kurtosis_births_dim2 <- c()
for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    hold_pers <- get(paste0("pers_", i, "_twos_birth"))
    if(!(length(hold_pers) <= 1) ){
      kurtosis_births_dim2 <- append(kurtosis_births_dim2, kurtosis(hold_pers))
    }
    if((length(hold_pers)) <= 1){
      kurtosis_births_dim2 <- append(kurtosis_births_dim2, 300)
    }
  }
  if(i %in% pers_bad_index2){
    kurtosis_births_dim2 <- append(kurtosis_births_dim2, 900)
  }
}
#########################Deaths############################
kurtosis_deaths_dim0 <- c()
for(i in seq(num_pers)){
  hold_pers <- get(paste0("pers_", i, "_zeros_death"))
  if(!(length(hold_pers) <= 1) ){
    kurtosis_deaths_dim0 <- append(kurtosis_deaths_dim0, kurtosis(hold_pers[1:(length(hold_pers)-1)]))
  } 
}

kurtosis_deaths_dim1 <- c()
for(i in seq(num_pers)){
  hold_pers <- get(paste0("pers_", i, "_ones_death"))
  if(!(length(hold_pers) <= 1) ){
    kurtosis_deaths_dim1 <- append(kurtosis_deaths_dim1, kurtosis(hold_pers))
  }
  if(length(hold_pers) <= 1){
   kurtosis_deaths_dim1 <- append(kurtosis_deaths_dim1, 200) 
  }
}

kurtosis_deaths_dim2 <- c()
for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    hold_pers <- get(paste0("pers_", i, "_twos_death"))
    if(!(length(hold_pers) <= 1) ){
      kurtosis_deaths_dim2 <- append(kurtosis_deaths_dim2, kurtosis(hold_pers))
    }
    if((length(hold_pers) <= 1)){
      kurtosis_deaths_dim2 <- append(kurtosis_deaths_dim2, 400)
    }
  }
  if(i %in% pers_bad_index2){
    kurtosis_deaths_dim2 <- append(kurtosis_deaths_dim2, 1000)
  }
}
```

##Store skewness, kurtosis in dataframe, export as CSV.
```{r} 
skewness_birth_dims <- data.frame("skew birth dim0" = skewness_births_dim0, "skew birth dim1" = skewness_births_dim1, "skew birth dim2" = skewness_births_dim2)

skewness_death_dims <- data.frame("skew death dim0" = skewness_deaths_dim0, "skew death dim1" = skewness_deaths_dim1, "skew death dim2" = skewness_deaths_dim2)

kurtosis_birth_dims <- data.frame("kurt birth dim0" = kurtosis_births_dim0, "kurt birth dim1" = kurtosis_births_dim1, "kurt birth dim2" = kurtosis_births_dim2)

kurtosis_death_dims <- data.frame("kurt death dim0" = kurtosis_deaths_dim0, "kurt death dim0" = kurtosis_deaths_dim1, "kurt death dim1" = kurtosis_deaths_dim2)

write.csv(skewness_birth_dims, file = "skewness_birth_dim012.csv")
write.csv(skewness_death_dims, file = "skewness_death_dim012.csv")
write.csv(kurtosis_birth_dims, file = "kurtosis_birth_dim012.csv")
write.csv(kurtosis_death_dims, file = "kurtosis_death_dim012.csv")
```

