---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
```{R}
library(sets)
library(moments)
```

```{r}
library(sets)
library(moments)
```

```{r}
temp <- as.matrix(read.csv("/Users/luke2/Desktop/REFERENCE-v3.csv", header = F)) 
```
#Load and store the persistence diagrams into the global environment.
```{r} 
directory <-"/Users/luke2/Desktop/TDA-MSRI-2018-master/everything/"

load_persistence_variable <- function(directory, labels, n){
  return(as.matrix(read.csv(file = paste0(directory, temp[n], ".csv")), header = T)[,-1])
}

num_pers <- 2001
#For loop will generate persistence variables.

for(i in seq(from = num_pers, to = 4000)){
  print(i)
  assign(paste0("persistence", i), load_persistence_variable(directory, labels, i))
}
```
##Compute_dim_births and Compute_dim_deaths
Unimportant helper function.
```{r} 
compute_zeros_birth <- function(n,a){ #Returns a list of birth times of 0 dimension.
  L <- c()
  for(i in seq(a)){
   L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
}
compute_zeros_death <- function(n,a){ #Returns a list of death times of 0 dimension
  L <- c()
  for(i in seq(a)){
   L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
}
###############################  
compute_ones_birth <- function(n,a,b){ #Returns a list of birth times of 1 dimension
  L <- c()
  for(i in seq(from=a+1, to=a+b)){
   L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
}
compute_ones_death <- function(n,a,b){
  L <- c()
  for(i in seq(from=a+1, to=a+b)){ #Returns a list of death times of 1 dimension.
   L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
}
#################
compute_twos_birth <- function(n,a,b,c){ #Returns a list of birth times of 2 dimensions.
  L <- c()
  for(i in seq(from=a+b+1, to=a+b+c)){
  L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
} 
compute_twos_death <- function(n,a,b,c){ #Returns a list od death times of 2 dimensions.
  L <- c()
  for(i in seq(from=a+b+1, to=a+b+c)){
  L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
} 
``` 
#Extract noise.
```{r} 
good_pers_index <- c()
pers_bad_index0 <- c()
pers_bad_index1 <- c()
pers_bad_index2 <- c()
pers_bad_index12 <- c()

for(i in seq(from = num_pers, to = 4000)){
  if(!is.na(Counting_Dimensions(i)[1]) & !is.na(Counting_Dimensions(i)[2]) & !is.na(Counting_Dimensions(i)[3]) ){
    good_pers_index <- append(good_pers_index, i)
  }
}
for(i in seq(from = num_pers, to = 4000)){
  if(is.na(Counting_Dimensions(i)[1])){
    pers_bad_index0 <- append(pers_bad_index0, i)
  }
  if(is.na(Counting_Dimensions(i)[2]) &  is.na(Counting_Dimensions(i)[3])){ #Check for files with no 0 dimensional features
    pers_bad_index12 <- append(pers_bad_index12, i)
  }
  if(is.na(Counting_Dimensions(i)[2])){ #Check for files with no 1 dimensional features
    pers_bad_index1 <- append(pers_bad_index1, i)
  }
  if(is.na(Counting_Dimensions(i)[3]) ){ #Check for files with no 2 dimensional features
    pers_bad_index2 <- append(pers_bad_index2, i)
  }
}

bad_files_dim1 <- c()
bad_files_dim2 <- c()
bad_files_dim12 <- c()

bad_normal <- c()
bad_af <- c()
bad_r <- c()
bad_o <- c()


for(i in pers_bad_index2){
  if(temp[i,2] == "N"){
    bad_normal <- append(bad_normal, i)
  }
  if(temp[i,2] == "A"){
    bad_af <- append(bad_af, i )
  }
  if(temp[i,2] == "~"){
    bad_r <- append(bad_r, i)
  }
  if(temp[i,2] == "O"){
    bad_o <- append(bad_o, i)
  }
}


for(i in pers_bad_index1){
  bad_files_dim1 <- append(bad_files_dim1, temp[i,2])
}

for(i in pers_bad_index2){
  bad_files_dim2 <- append(bad_files_dim2, temp[i, 2])
  
}

for(i in pers_bad_index12){
  bad_files_dim12 <- append(bad_files_dim12, temp[i,2])
}
```
#normal, af, r, o files
```{r}
normal_files <- c() 
for(i in good_pers_index){
  if(temp[i,2] == "N"){
    normal_files <- append(normal_files, i)
  }
}

af_files <- c()
for(i in good_pers_index){
  if(temp[i,2] == "A"){
    af_files <- append(af_files, i)
  }
}

r_files <- c()
for(i in good_pers_index){
  if(temp[i,2] == "~"){
    r_files <- append(r_files, i)
  }
}

o_files <- c() 
for(i in good_pers_index){
  if(temp[i,2] == "O"){
    o_files <- append(o_files, i) 
  } 
}
```
#Counting Dimensions
Unimportant helper function. Counts the number of zeros, ones and two dimensional features in the persistence diagrams, given whatever persistence diagram you want.
```{r} 
Counting_Dimensions <- function(n){
  tempFrame <- data.frame("Dimension" = get(paste0("persistence", n))[,1], "Birth" = get(paste0("persistence", n))[,2], "Death" = get(paste0("persistence", n))[,3])  
  return(table(tempFrame$Dimension))
}
```
##Export the labels.
```{R} 
labels <- c()
for(i in seq(from = num_pers, to = 4000)){
  labels <- append(labels, temp[i,1])
} 

classes <- c() 
for(i in seq(from = num_pers, to = 4000)){
  classes <- append(classes, temp[i,2])
}
```
##Extract_dim_biths and Extract_dim_deaths
Extracts the zero, one and two dimensional birth and death features.
```{r}
Extract_Birth_Zeros <- function(n){ #n is desired dimension
    p <- c() 
    a <- Counting_Dimensions(n)[1]
    #b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth variables.
    assign(paste0("pers_", n, "_zeros_birth"), compute_zeros_birth(n,a))
    p <- append(p, get(paste0("pers_", n, "_zeros_birth")))
    return(p)
}
Extract_Death_Zeros <- function(n){ #n is desired dimension
    p <- c()
    a <- Counting_Dimensions(n)[1]
    #b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables
    assign(paste0("pers_", n, "_zeros_death"), compute_zeros_death(n,a))
    p <- append(p, get(paste0("pers_", n, "_zeros_death")))
    return(p)
    # k <- 0
    # assign(k, compute_zeros_death(n,a))
    # return(k)
}
Extract_Birth_Ones <- function(n){ #n is desired dimension
    p<- c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables.
    assign(paste0("pers_", n, "_ones_birth"), compute_ones_birth(n,a,b)) 
    p <- append(p, get(paste0("pers_", n, "_ones_birth")))
    return(p)
}
Extract_Death_Ones <- function(n){ #n is desired dimension
    p<- c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables.
    assign(paste0("pers_", n, "_ones_death"), compute_ones_death(n,a,b)) 
    p <- append(p, get(paste0("pers_", n, "_ones_death")))
    return(p)
}
Extract_Birth_Twos <- function(n){ #n is desired dimension
    p<-c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    c <- Counting_Dimensions(n)[3]
    
    #Assigns birth variables.
    assign(paste0("pers_", n, "_twos_birth"), compute_twos_birth(n,a,b,c)) 
    p <- append(p, get(paste0("pers_", n, "_twos_birth")))
    return(p)    
}
Extract_Death_Twos <- function(n){ #n is desired dimension
    p<-c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables. 
    assign(paste0("pers_", n, "_twos_death"), compute_twos_death(n,a,b,c)) 
    p <- append(p, get(paste0("pers_", n, "_twos_death")))
    return(p)     
} 
```
##Store_birth_dim and Store_death_dim
Stores the zero, one and two dimensional birth and death features of each persistence diagram in your global environment. You will have many, many variables in your environment.
```{r}
#####Clean function#####
for(i in seq(from = num_pers, to = 4000)){ 
  if(i %in% good_pers_index){
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv) 
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_birth"), Extract_Birth_Ones(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_death"), Extract_Death_Ones(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_birth"), Extract_Birth_Twos(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_death"), Extract_Death_Twos(i),envir=.GlobalEnv)
  }
  if(i %in% pers_bad_index1 & !(i %in%  pers_bad_index2)){#Has no 1 dimensional features, but 2 dimension features
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_birth"), Extract_Birth_Twos(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_death"), Extract_Death_Twos(i),envir=.GlobalEnv)
  }
  if((i %in% pers_bad_index2)){#Has 1 dimensional features but no 2 dimensional features
    print(i)
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_birth"), Extract_Birth_Ones(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_death"), Extract_Death_Ones(i),envir=.GlobalEnv)    
  }
  if(i %in% pers_bad_index12){#Has no 1 or 2 dimensional features
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)    
  }
}

```
##Calculate sum of lifetimes
The lifetimes are summed across the dimensions per each persistence diagram.
```{r} 
#Lifetimes for d imension 0 
lifetimes_dim0 <- c()
for(i in seq(num_pers)){
  lifetime <- sum(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)])
  lifetimes_dim0 <- append(lifetimes_dim0, lifetime)
}

#Lifetimes for dimension 1.
lifetimes_dim1 <- c()
for(i in seq(num_pers)){
  lifetime <- sum(get(paste0("pers_", i, "_ones_death"))) - sum(get((paste0("pers_", i, "_ones_birth"))))
  lifetimes_dim1 <- append(lifetimes_dim1, lifetime)
}

#Lifetimes for dimension 2.
lifetimes_dim2 <- c()
for(i in seq(num_pers)){
  if(i %in% good_pers_index){
    lifetime <- sum((get(paste0("pers_", i, "_twos_death")))) - sum(get((paste0("pers_", i, "_twos_birth"))))
    lifetimes_dim2 <- append(lifetimes_dim2, lifetime)
  }
  
  else{
    lifetime <- 400
    lifetimes_dim2 <- append(lifetimes_dim2, lifetime)
  }
}
```
##Oraganize lifetime data into a dataframe, export as CSV.
```{r} 
lifetimedata <- data.frame("Lifetime_dim0" = lifetimes_dim0, "Lifetime_dim1" = lifetimes_dim1, "Lifetime_dim2" = lifetimes_dim2)
write.csv(lifetimedata, file = "Lifetimes_dim_0_1_2.csv")
```
##Caclulate maximum hole lifetimes
Calculates the maximum lifetime of each feature across all dimensions per persistence diagram.
```{r} 
maxs_dim0 <- c()
for(i in seq(nump_pers)){
  hold_lifetimes <- c()
  print(i)
  for(j in seq(length(get(paste0("pers_", i, "_zeros_death"))))){
    hold_lifetimes <- append(hold_lifetimes, (get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
 
   maxs_dim0 <- append(maxs_dim0, max(hold_lifetimes))
} 

maxs_dim1 <- c()
for(i in seq(num_pers)){
  hold_lifetimes <- c()
  print(i) 
  for(j in seq(length(get(paste0("pers_", i, "_ones_death"))))){
    hold_lifetimes <- append(hold_lifetimes, (get(paste0("pers_", i, "_ones_death"))[j] - get(paste0("pers_", i, "_ones_birth"))))
    }
 
   maxs_dim1 <- append(maxs_dim1, max(hold_lifetimes))
}
maxs_dim2 <- c()
for(i in seq(num_pers)){
  hold_lifetimes <- c()
  print(i)
  for(j in seq(length(get(paste0("pers_", i, "_twos_death"))))){
    hold_lifetimes <- append(hold_lifetimes, (get(paste0("pers_", i, "_twos_death"))[j] - get(paste0("pers_", i, "_twos_birth"))))
    }
 
   maxs_dim2 <- append(maxs_dim2, max(hold_lifetimes))
}
```
##Convert to dataframe, export as CSV.
```{r}
max_lifetimes <- data.frame("Max_life_dim0" = maxs_dim0, "Max_life_dim1" = maxs_dim1, "Max_life_dim2" = maxs_dim2)
write.csv(max_lifetimes, file = "Maximum_lifetimes_all_dims.csv")
```
