---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r}
library(sets)
library(moments)
```

```{r}
temp <- as.matrix(read.csv("/Users/luke/Desktop/REFERENCE-v3.csv", header = F)) 
```

#Load and store the persistence diagrams into the global environment.
```{r} 
directory <-"/Users/luke/Desktop/Cor_Rest_of_points_dim012/"

load_persistence_variable <- function(directory, n){
  return(as.matrix(read.csv(file = paste0(directory, "rest_of_points", temp[n], ".csv")), header = T)[,-1])
}

num_pers <- 2001
#For loop will generate persistence variables.

for(i in seq(from = num_pers, to = 4000)){
  print(i)
  assign(paste0("persistence", i), load_persistence_variable(directory, i))
}
```

##Counting Dimensions
Unimportant helper function. Counts the number of zeros, ones and two dimensional features in the persistence diagrams, given whatever persistence diagram you want.
```{r} 
Counting_Dimensions <- function(n){
  tempFrame <- data.frame("Dimension" = get(paste0("persistence", n))[,1], "Birth" = get(paste0("persistence", n))[,2], "Death" = get(paste0("persistence", n))[,3])  
  return(table(tempFrame$Dimension))
}
```

#Extract noise.
```{r} 
good_pers_index <- c()
pers_bad_index0 <- c()
pers_bad_index1 <- c()
pers_bad_index2 <- c()
pers_bad_index12 <- c()

for(i in seq(from = num_pers, to = 4000)){
  if(!is.na(Counting_Dimensions(i)[1]) & !is.na(Counting_Dimensions(i)[2]) & !is.na(Counting_Dimensions(i)[3]) ){
    good_pers_index <- append(good_pers_index, i)
  }
}
for(i in seq(from = num_pers, to = 4000)){
  if(is.na(Counting_Dimensions(i)[1])){
    pers_bad_index0 <- append(pers_bad_index0, i)
  }
  if(is.na(Counting_Dimensions(i)[2]) &  is.na(Counting_Dimensions(i)[3])){ #Check for files with no 0 dimensional features
    pers_bad_index12 <- append(pers_bad_index12, i)
  }
  if(is.na(Counting_Dimensions(i)[2])){ #Check for files with no 1 dimensional features
    pers_bad_index1 <- append(pers_bad_index1, i)
  }
  if(is.na(Counting_Dimensions(i)[3]) ){ #Check for files with no 2 dimensional features
    pers_bad_index2 <- append(pers_bad_index2, i)
  }
}

bad_files_dim1 <- c()
bad_files_dim2 <- c()
bad_files_dim12 <- c()

bad_normal <- c()
bad_af <- c()
bad_r <- c()
bad_o <- c()


for(i in pers_bad_index2){
  if(temp[i,2] == "N"){
    bad_normal <- append(bad_normal, i)
  }
  if(temp[i,2] == "A"){
    bad_af <- append(bad_af, i )
  }
  if(temp[i,2] == "~"){
    bad_r <- append(bad_r, i)
  }
  if(temp[i,2] == "O"){
    bad_o <- append(bad_o, i)
  }
}


for(i in pers_bad_index1){
  bad_files_dim1 <- append(bad_files_dim1, temp[i,2])
}

for(i in pers_bad_index2){
  bad_files_dim2 <- append(bad_files_dim2, temp[i, 2])
  
}

for(i in pers_bad_index12){
  bad_files_dim12 <- append(bad_files_dim12, temp[i,2])
}
```

#normal, af, r, o files
```{r}
normal_files <- c() 
for(i in good_pers_index){
  if(temp[i,2] == "N"){
    normal_files <- append(normal_files, i)
  }
}

af_files <- c()
for(i in good_pers_index){
  if(temp[i,2] == "A"){
    af_files <- append(af_files, i)
  }
}

r_files <- c()
for(i in good_pers_index){
  if(temp[i,2] == "~"){
    r_files <- append(r_files, i)
  }
}

o_files <- c() 
for(i in good_pers_index){
  if(temp[i,2] == "O"){
    o_files <- append(o_files, i) 
  } 
}
```

##Export the labels.
```{R} 
labels <- c()
for(i in seq(from = num_pers, to = 4000)){
  labels <- append(labels, temp[i,1])
} 

classes <- c() 
for(i in seq(from = num_pers, to = 4000)){
  classes <- append(classes, temp[i,2])
}
```


##Compute_dim_births and Compute_dim_deaths
Unimportant helper function.
```{r} 
compute_zeros_birth <- function(n,a){ #Returns a list of birth times of 0 dimension.
  L <- c()
  for(i in seq(a)){
   L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
}
compute_zeros_death <- function(n,a){ #Returns a list of death times of 0 dimension
  L <- c()
  for(i in seq(a)){
   L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
}
###############################  
compute_ones_birth <- function(n,a,b){ #Returns a list of birth times of 1 dimension
  L <- c()
  for(i in seq(from=a+1, to=a+b)){
   L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
}
compute_ones_death <- function(n,a,b){
  L <- c()
  for(i in seq(from=a+1, to=a+b)){ #Returns a list of death times of 1 dimension.
   L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
}
#################
compute_twos_birth <- function(n,a,b,c){ #Returns a list of birth times of 2 dimensions.
  L <- c()
  for(i in seq(from=a+b+1, to=a+b+c)){
  L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
} 
compute_twos_death <- function(n,a,b,c){ #Returns a list od death times of 2 dimensions.
  L <- c()
  for(i in seq(from=a+b+1, to=a+b+c)){
  L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
} 
```  
 
##Extract_dim_biths and Extract_dim_deaths
Extracits the zero, one and two dimensional birth and death features.
```{r}
Extract_Birth_Zeros <- function(n){ #n is desired dimension
    p <- c() 
    a <- Counting_Dimensions(n)[1]
    #b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth variables.
    assign(paste0("pers_", n, "_zeros_birth"), compute_zeros_birth(n,a))
    p <- append(p, get(paste0("pers_", n, "_zeros_birth")))
    return(p)
}
Extract_Death_Zeros <- function(n){ #n is desired dimension
    p <- c()
    a <- Counting_Dimensions(n)[1]
    #b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables
    assign(paste0("pers_", n, "_zeros_death"), compute_zeros_death(n,a))
    p <- append(p, get(paste0("pers_", n, "_zeros_death")))
    return(p)
    # k <- 0
    # assign(k, compute_zeros_death(n,a))
    # return(k)
}
Extract_Birth_Ones <- function(n){ #n is desired dimension
    p<- c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables.
    assign(paste0("pers_", n, "_ones_birth"), compute_ones_birth(n,a,b)) 
    p <- append(p, get(paste0("pers_", n, "_ones_birth")))
    return(p)
}
Extract_Death_Ones <- function(n){ #n is desired dimension
    p<- c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables.
    assign(paste0("pers_", n, "_ones_death"), compute_ones_death(n,a,b)) 
    p <- append(p, get(paste0("pers_", n, "_ones_death")))
    return(p)
}
Extract_Birth_Twos <- function(n){ #n is desired dimension
    p<-c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    c <- Counting_Dimensions(n)[3]
    
    #Assigns birth variables.
    assign(paste0("pers_", n, "_twos_birth"), compute_twos_birth(n,a,b,c)) 
    p <- append(p, get(paste0("pers_", n, "_twos_birth")))
    return(p)    
}
Extract_Death_Twos <- function(n){ #n is desired dimension
    p<-c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables. 
    assign(paste0("pers_", n, "_twos_death"), compute_twos_death(n,a,b,c)) 
    p <- append(p, get(paste0("pers_", n, "_twos_death")))
    return(p)     
} 
```

##Store_birth_dim and Store_death_dim
Stores the zero, one and two dimensional birth and death features of each persistence diagram in your global environment. You will have many, many variables in your environment.
```{r}
#####Clean function#####
for(i in seq(from = num_pers, to = 4000)){ 
  if(i %in% good_pers_index){
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv) 
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_birth"), Extract_Birth_Ones(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_death"), Extract_Death_Ones(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_birth"), Extract_Birth_Twos(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_death"), Extract_Death_Twos(i),envir=.GlobalEnv)
  }
  if(i %in% pers_bad_index1 & !(i %in%  pers_bad_index2)){#Has no 1 dimensional features, but 2 dimension features
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_birth"), Extract_Birth_Twos(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_twos_death"), Extract_Death_Twos(i),envir=.GlobalEnv)
  }
  if((i %in% pers_bad_index2)){#Has 1 dimensional features but no 2 dimensional features
    print(i)
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_birth"), Extract_Birth_Ones(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_ones_death"), Extract_Death_Ones(i),envir=.GlobalEnv)    
  }
  if(i %in% pers_bad_index12){#Has no 1 or 2 dimensional features
    assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
    assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)    
  }
}

```

##Mean and SD of births across dimensions.
These functions below store the mean and standard deviation values across the birth values for dimensions one and two. We skip the births of dimension 0, since they're all 0s.
```{r}
mean_Births_Normal_dim_1 <- c()
mean_Births_Normal_dim_2 <- c()

sd_Births_Normal_dim_1 <- c()
sd_Births_Normal_dim_2 <- c()

mean_Births_AF_dim_1 <- c()
mean_Births_AF_dim_2 <- c()

sd_Births_AF_dim_1 <- c()
sd_Births_AF_dim_2 <- c()

mean_Births_Rand_dim_1 <- c()
mean_Births_Rand_dim_2 <- c()

sd_Births_Rand_dim_1 <- c()
sd_Births_Rand_dim_2 <- c()

mean_Births_O_dim_1 <- c()
mean_Births_O_dim_2 <- c()

sd_Births_O_dim_1 <- c()
sd_Births_O_dim_2 <- c()


bad_mean_Births_Normal_dim_1 <- c()
bad_sd_Births_Normal_dim_1 <- c()

bad_mean_Births_AF_dim_1 <- c()
bad_sd_Births_AF_dim_1 <- c()

bad_mean_Births_Rand_dim_1 <- c()
bad_sd_Births_Rand_dim_1 <- c()

bad_mean_Births_O_dim_1 <- c()
bad_sd_Births_O_dim_1 <- c()

bad_mean_Births_Normal_dim_2 <- c()
bad_sd_Births_Normal_dim_2 <- c()

bad_mean_Births_AF_dim_2 <- c()
bad_sd_Births_AF_dim_2 <- c()

bad_mean_Births_Rand_dim_2 <- c()
bad_sd_Births_Rand_dim_2 <- c()

bad_mean_Births_O_dim_2 <- c()
bad_sd_Births_O_dim_2 <- c()


for(i in seq(from = num_pers, to = 4000)){
  if(i %in% good_pers_index){ 
    if(i %in% normal_files){
      mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))
      print(mean(get(paste0("pers_", i, "_ones_birth"))))

      mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 50)
    }
    if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
      sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
    }
    else{
      sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 80)
    }
}
    
    if(i %in% af_files){
  mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

  mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
    else{
      sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 50)
    }
  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 80)
  }
}

    if(i %in% r_files){
      mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, mean(as.numeric(get(paste0("pers_", i, "_ones_birth")))))
      # if(is.na(mean_Births_Rand_dim_1[i])){
      #   mean_Births_Rand_dim_1[i] <- mean(as.numeric(get(paste0("pers_", i, "_ones_birth"))))
      # }
      # print(mean_Births_Rand_dim_1[i])

      mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2, mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 50)
  }

  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 80)
  }
}

    if(i %in% o_files){
    mean_Births_O_dim_1 <- append(mean_Births_O_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    mean_Births_O_dim_2 <- append(mean_Births_O_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_O_dim_1 <- append(sd_Births_O_dim_1, 50)
  }

  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_O_dim_2 <- append(sd_Births_O_dim_2, 80)
  }
}
  }
  
  if(i %in% pers_bad_index2){
    print(i)
    if(temp[i,2] == "N"){
      bad_mean_Births_Normal_dim_1 <- append(bad_mean_Births_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))
      
      if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
        bad_sd_Births_Normal_dim_1 <- append(bad_sd_Births_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
      }
      else{
        bad_sd_Births_Normal_dim_1 <- append(bad_sd_Births_Normal_dim_1,80)
      }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        bad_mean_Births_Normal_dim_1 <- append(bad_mean_Births_Normal_dim_1, 100)
        bad_sd_Births_Normal_dim_1 <- append(bad_sd_Births_Normal_dim_1, 700)
    }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        bad_mean_Births_Normal_dim_2 <- append(bad_mean_Births_Normal_dim_2, 300)
        bad_sd_Births_Normal_dim_2 <- append(bad_sd_Births_Normal_dim_2, 1000)
    }
      if(i %in% pers_bad_index12){ #10000
        bad_mean_Births_Normal_dim_1 <- append(bad_mean_Births_Normal_dim_1, 100)
        bad_mean_Births_Normal_dim_2 <- append(bad_mean_Births_Normal_dim_2, 300)
        bad_sd_Births_Normal_dim_1 <- append(bad_sd_Births_Normal_dim_1, 700)
        bad_sd_Births_Normal_dim_2 <- append(bad_sd_Births_Normal_dim_2, 1000)
    }
  }

    if(temp[i,2] == "A"){
      bad_mean_Births_AF_dim_1 <- append(bad_mean_Births_AF_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      bad_sd_Births_AF_dim_1 <- append(bad_sd_Births_AF_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      bad_sd_Births_AF_dim_1 <- append(bad_sd_Births_AF_dim_1, 80)
    }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        bad_mean_Births_AF_dim_1 <- append(bad_mean_Births_AF_dim_1, 100)
        bad_sd_Births_AF_dim_1 <- append(bad_sd_Births_AF_dim_1, 700)
      }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        bad_mean_Births_AF_dim_2 <- append(bad_mean_Births_AF_dim_2, 300)
        bad_sd_Births_AF_dim_2 <- append(bad_sd_Births_AF_dim_2, 1000)
      }
      if(i %in% pers_bad_index12){ #10000
        bad_mean_Births_AF_dim_1 <- append(bad_mean_Births_AF_dim_1, 100)
        bad_mean_Births_AF_dim_2 <- append(bad_mean_Births_AF_dim_2, 300)
        bad_sd_Births_AF_dim_1 <- append(bad_sd_Births_AF_dim_1, 700)
        bad_sd_Births_AF_dim_2 <- append(bad_sd_Births_AF_dim_2, 1000)
    }
  }

    if(temp[i,2] == "~"){
      bad_mean_Births_Rand_dim_1 <- append(bad_mean_Births_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      bad_sd_Births_Rand_dim_1 <- append(bad_sd_Births_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      bad_sd_Births_Rand_dim_1 <- append(bad_sd_Births_Rand_dim_1, 80)
    } 
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      bad_mean_Births_Rand_dim_1 <- append(bad_mean_Births_Rand_dim_1, 100)
      bad_sd_Births_Rand_dim_1 <- append(bad_sd_Births_Rand_dim_1, 700)
  }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      bad_mean_Births_Rand_dim_2 <- append(bad_mean_Births_Rand_dim_2, 300)
      bad_sd_Births_Rand_dim_2 <- append(bad_sd_Births_Rand_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      bad_mean_Births_Rand_dim_1 <- append(bad_mean_Births_Rand_dim_1, 100)
      bad_mean_Births_Rand_dim_2 <- append(bad_mean_Births_Rand_dim_2, 300)
      bad_sd_Births_Rand_dim_1 <- append(bad_sd_Births_Rand_dim_1, 700)
      bad_sd_Births_Rand_dim_2 <- append(bad_sd_Births_Rand_dim_2, 1000)
    }
    }
     
    if(temp[i,2] == "O"){
      bad_mean_Births_O_dim_1 <- append(bad_mean_Births_O_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))
      
    if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
      bad_sd_Births_O_dim_1 <- append(bad_sd_Births_O_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
    }
    else{
      bad_sd_Births_O_dim_1 <- append(bad_sd_Births_O_dim_1, 80)
    }      
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      bad_mean_Births_O_dim_1 <- append(bad_mean_Births_O_dim_1, 100)
      bad_sd_Births_O_dim_1 <- append(bad_sd_Births_O_dim_1, 700)
    }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      bad_mean_Births_O_dim_1 <- append(bad_mean_Births_O_dim_1, 100)
      bad_sd_Births_O_dim_1 <- append(bad_sd_Births_O_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      bad_mean_Births_O_dim_2 <- append(bad_mean_Births_O_dim_2, 300)
      bad_sd_Births_O_dim_2 <- append(bad_sd_Births_O_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      bad_mean_Births_O_dim_1 <- append(bad_mean_Births_O_dim_1, 100)
      bad_mean_Births_O_dim_2 <- append(bad_mean_Births_O_dim_2, 300)
      bad_sd_Births_O_dim_1 <- append(bad_sd_Births_O_dim_1, 700)
      bad_sd_Births_O_dim_2 <- append(bad_sd_Births_O_dim_2, 1000)
    }
  }
  }
}
```

##Mean and SD of deaths across dimensions.
These functions below store the mean and standard deviation values across the death values for dimensions zero, one and two.
```{r}
mean_Deaths_Normal_dim_0 <- c()
mean_Deaths_Normal_dim_1 <- c()
mean_Deaths_Normal_dim_2 <- c() 

sd_Deaths_Normal_dim_0 <- c()
sd_Deaths_Normal_dim_1 <- c()
sd_Deaths_Normal_dim_2 <- c()

mean_Deaths_AF_dim_0 <- c()
mean_Deaths_AF_dim_1 <- c()
mean_Deaths_AF_dim_2 <- c()

sd_Deaths_AF_dim_0 <- c()
sd_Deaths_AF_dim_1 <- c()
sd_Deaths_AF_dim_2 <- c()

mean_Deaths_Rand_dim_0 <- c()
mean_Deaths_Rand_dim_1 <- c()
mean_Deaths_Rand_dim_2 <- c()

sd_Deaths_Rand_dim_0 <- c()
sd_Deaths_Rand_dim_1 <- c()
sd_Deaths_Rand_dim_2 <- c()

mean_Deaths_O_dim_0 <- c()
mean_Deaths_O_dim_1 <- c()
mean_Deaths_O_dim_2 <- c()

sd_Deaths_O_dim_0 <- c()
sd_Deaths_O_dim_1 <- c()
sd_Deaths_O_dim_2 <- c()

bad_mean_Deaths_Normal_dim_0 <- c()
bad_sd_Deaths_Normal_dim_0 <- c()

bad_mean_Deaths_Normal_dim_1 <- c()
bad_sd_Deaths_Normal_dim_1 <- c()

bad_mean_Deaths_Normal_dim_2 <- c()
bad_sd_Deaths_Normal_dim_2 <- c()

bad_mean_Deaths_AF_dim_0 <- c()
bad_sd_Deaths_AF_dim_0 <- c()

bad_mean_Deaths_AF_dim_1 <- c()
bad_sd_Deaths_AF_dim_1 <- c()

bad_mean_Deaths_AF_dim_2 <- c()
bad_sd_Deaths_AF_dim_2 <- c()

bad_mean_Deaths_Rand_dim_0 <- c()
bad_sd_Deaths_Rand_dim_0 <- c()

bad_mean_Deaths_Rand_dim_1 <- c()
bad_sd_Deaths_Rand_dim_1 <- c()

bad_mean_Deaths_Rand_dim_2 <- c()
bad_sd_Deaths_Rand_dim_2 <- c()

bad_mean_Deaths_O_dim_0 <- c()
bad_sd_Deaths_O_dim_0 <- c()

bad_mean_Deaths_O_dim_1 <- c()
bad_sd_Deaths_O_dim_1 <- c()

bad_mean_Deaths_O_dim_2 <- c()
bad_sd_Deaths_O_dim_2 <- c()

for(i in seq(from = num_pers, to = 4000)){
  if(i %in% good_pers_index){
    if(i %in% normal_files){
  mean_Deaths_Normal_dim_0 <- append(mean_Deaths_Normal_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  if(length(get(paste0("pers_", i, "_zeros_death")) != 1)){
    sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
    sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1,80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 30)
  }
}

    if(i %in% af_files){
  mean_Deaths_AF_dim_0 <- append(mean_Deaths_AF_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_AF_dim_2 <- append(mean_Deaths_AF_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  
  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
    sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 30)
  }
}

    if(i %in% r_files){
  mean_Deaths_Rand_dim_0 <- append(mean_Deaths_Rand_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_Rand_dim_2 <- append(mean_Deaths_Rand_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  
  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
  sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 30)
  }
}

    if(i %in% o_files){
  mean_Deaths_O_dim_0 <- append(mean_Deaths_O_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_O_dim_1 <- append(mean_Deaths_O_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_O_dim_2 <- append(mean_Deaths_O_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))

  
  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_O_dim_0 <- append(sd_Deaths_O_dim_0, 50)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
  sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_O_dim_1 <- append(sd_Deaths_O_dim_1, 80)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_O_dim_2 <- append(sd_Deaths_O_dim_2, 30)
  }
}
  }

  if(i %in% pers_bad_index2){ 
    if(temp[i,2] == "N"){
      bad_mean_Deaths_Normal_dim_0 <- append(bad_mean_Deaths_Normal_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      bad_mean_Deaths_Normal_dim_1 <- append(bad_mean_Deaths_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
      
      if(length(get(paste0("pers_", i, "_zeros_death")) != 1)){
        bad_sd_Deaths_Normal_dim_0 <- append(bad_sd_Deaths_Normal_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      }
      else{
        bad_sd_Deaths_Normal_dim_0 <- append(bad_sd_Deaths_Normal_dim_0, 50)
      }
      if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
        bad_sd_Deaths_Normal_dim_1 <- append(bad_sd_Deaths_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
      }
      else{
        bad_sd_Deaths_Normal_dim_1 <- append(bad_sd_Deaths_Normal_dim_1,80)
      }
      
      if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        bad_mean_Deaths_Normal_dim_1 <- append(bad_mean_Deaths_Normal_dim_1, 100)
        bad_sd_Deaths_Normal_dim_1 <- append(bad_sd_Deaths_Normal_dim_1, 700)
      }
      if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        print(i)
        bad_mean_Deaths_Normal_dim_2 <- append(bad_mean_Deaths_Normal_dim_2, 300)
        bad_sd_Deaths_Normal_dim_2 <- append(bad_sd_Deaths_Normal_dim_2, 1000)
    }
      if(i %in% pers_bad_index12){ #10000
        bad_mean_Deaths_Normal_dim_1 <- append(bad_mean_Deaths_Normal_dim_1, 100)
        bad_mean_Deaths_Normal_dim_2 <- append(bad_mean_Deaths_Normal_dim_2, 300)
        bad_sd_Deaths_Normal_dim_1 <- append(bad_sd_Deaths_Normal_dim_1, 700)
        bad_sd_Deaths_Normal_dim_2 <- append(bad_sd_Deaths_Normal_dim_2, 1000)
    }
  }

    if(temp[i,2] == "A"){
      bad_mean_Deaths_AF_dim_0 <- append(bad_mean_Deaths_AF_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      bad_mean_Deaths_AF_dim_1 <- append(bad_mean_Deaths_AF_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

    if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
      bad_sd_Deaths_AF_dim_0 <- append(bad_sd_Deaths_AF_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
    else{
      bad_sd_Deaths_AF_dim_0 <- append(bad_sd_Deaths_AF_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
      bad_sd_Deaths_AF_dim_1 <- append(bad_sd_Deaths_AF_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
    }
    else{
      bad_sd_Deaths_AF_dim_1 <- append(bad_sd_Deaths_AF_dim_1, 80)
    }
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
        bad_mean_Deaths_AF_dim_1 <- append(bad_mean_Deaths_AF_dim_1, 100)
        bad_sd_Deaths_AF_dim_1 <- append(bad_sd_Deaths_AF_dim_1, 700)
      }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
        print(i)
        bad_mean_Deaths_AF_dim_2 <- append(bad_mean_Deaths_AF_dim_2, 300)
        bad_sd_Deaths_AF_dim_2 <- append(bad_sd_Deaths_AF_dim_2, 1000)
      }
    if(i %in% pers_bad_index12){ #10000
        bad_mean_Deaths_AF_dim_1 <- append(bad_mean_Deaths_AF_dim_1, 100)
        bad_mean_Deaths_AF_dim_2 <- append(bad_mean_Deaths_AF_dim_2, 300)
        bad_sd_Deaths_AF_dim_1 <- append(bad_sd_Deaths_AF_dim_1, 700)
        bad_sd_Deaths_AF_dim_2 <- append(bad_sd_Deaths_AF_dim_2, 1000)
    }
  }

    if(temp[i,2] == "~"){
      bad_mean_Deaths_Rand_dim_0 <- append(bad_mean_Deaths_Rand_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      bad_mean_Deaths_Rand_dim_1 <- append(bad_mean_Deaths_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
      
    if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
      bad_sd_Deaths_Rand_dim_0 <- append(bad_sd_Deaths_Rand_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
    else{
      bad_sd_Deaths_Rand_dim_0 <- append(bad_sd_Deaths_Rand_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
      bad_sd_Deaths_Rand_dim_1 <- append(bad_sd_Deaths_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
    }
    else{
      bad_sd_Deaths_Rand_dim_1 <- append(bad_sd_Deaths_Rand_dim_1, 80)
    }      
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      bad_mean_Deaths_Rand_dim_1 <- append(bad_mean_Deaths_Rand_dim_1, 100)
      bad_sd_Deaths_Rand_dim_1 <- append(bad_sd_Deaths_Rand_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features 
      print(i)
      bad_mean_Deaths_Rand_dim_2 <- append(bad_mean_Deaths_Rand_dim_2, 300)
      bad_sd_Deaths_Rand_dim_2 <- append(bad_sd_Deaths_Rand_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      bad_mean_Deaths_Rand_dim_1 <- append(bad_mean_Deaths_Rand_dim_1, 100)
      bad_mean_Deaths_Rand_dim_2 <- append(bad_mean_Deaths_Rand_dim_2, 300)
      bad_sd_Deaths_Rand_dim_1 <- append(bad_sd_Deaths_Rand_dim_1, 700)
      bad_sd_Deaths_Rand_dim_2 <- append(bad_sd_Deaths_Rand_dim_2, 1000)
    }
  }
    
    if(temp[i,2] == "O"){
      bad_mean_Deaths_O_dim_0 <- append(bad_mean_Deaths_O_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
      bad_mean_Deaths_O_dim_1 <- append(bad_mean_Deaths_O_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))

    if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){ 
      bad_sd_Deaths_O_dim_0 <- append(bad_sd_Deaths_O_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
    }
    else{
      bad_sd_Deaths_O_dim_0 <- append(bad_sd_Deaths_O_dim_0, 50)
    }
    if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
      bad_sd_Deaths_O_dim_1 <- append(bad_sd_Deaths_O_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
    }
    else{
      bad_sd_Deaths_O_dim_1 <- append(bad_sd_Deaths_O_dim_1, 80)
    }      
      
    if(i %in% pers_bad_index1){ #100 is the random statistic assigned to those missing 1 dimensional features.
      bad_mean_Deaths_O_dim_1 <- append(bad_mean_Deaths_O_dim_1, 100)
      bad_sd_Deaths_O_dim_1 <- append(bad_sd_Deaths_O_dim_1, 700)
    }
    if(i %in% pers_bad_index2){ #1000 is the random statistic assigned to those missing 2 dimensional features
      print(i)
      bad_mean_Deaths_O_dim_2 <- append(bad_mean_Deaths_O_dim_2, 300)
      bad_sd_Deaths_O_dim_2 <- append(bad_sd_Deaths_O_dim_2, 1000)
    }
    if(i %in% pers_bad_index12){ #10000
      bad_mean_Deaths_O_dim_1 <- append(bad_mean_Deaths_O_dim_1, 100)
      bad_mean_Deaths_O_dim_2 <- append(bad_mean_Deaths_O_dim_2, 300)
      bad_sd_Deaths_O_dim_1 <- append(bad_sd_Deaths_O_dim_1, 700)
      bad_sd_Deaths_O_dim_2 <- append(bad_sd_Deaths_O_dim_2, 1000)
    }
  }
  } 
}
```

##The good mistake: Reappend and get yo fucking shit together 
```{r}
################################ dim 0 ################################  
total_means_births_dim0 <-seq(0,0,length.out=2000)
total_sd_births_dim0 <- seq(0,0,length.out=2000) 

total_means_deaths_dim0 <- c()
total_sd_deaths_dim0 <-c()

#Store the death 0 dimensional means.
for(i in seq(from = 2001, to = 4000)){ #Organize the death means of 0 dimension.
  if(i %in% normal_files){
    total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_Normal_dim_0[which(normal_files == i)])
  }
  if(i %in% af_files){
    total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_AF_dim_0[which(af_files == i)])
  }
  if(i %in% r_files){
    total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_Rand_dim_0[which(r_files == i)])
  }
  if(i %in% o_files){
    total_means_deaths_dim0 <- append(total_means_deaths_dim0, mean_Deaths_O_dim_0[which(o_files == i)])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_means_deaths_dim0 <- append(total_means_deaths_dim0, bad_mean_Deaths_Normal_dim_0[which(bad_normal == i)])
    }
    if(temp[i,2] == "A"){
      total_means_deaths_dim0 <- append(total_means_deaths_dim0, bad_mean_Deaths_AF_dim_0[which(bad_af == i)])
    }
    if(temp[i,2] == "~"){
      total_means_deaths_dim0 <- append(total_means_deaths_dim0, bad_mean_Deaths_Rand_dim_0[which(bad_r == i)])
    }
    if(temp[i,2] == "O"){
      total_means_deaths_dim0 <- append(total_means_deaths_dim0, bad_mean_Deaths_O_dim_0[which(bad_o == i)])
    }
  }
}
#Store the death 0 dimensional sd.

for(i in seq(from = 2001, to = 4000)){ #Organize the deaht sd of 0 dimension.
  if(i %in% normal_files){
    total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_Normal_dim_0[which(normal_files == i)])
  }
  if(i %in% af_files){
    total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_AF_dim_0[which(af_files == i)])
  }
  if(i %in% r_files){
    total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_Rand_dim_0[which(r_files == i)])
  }
  if(i %in% o_files){
    total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, sd_Deaths_O_dim_0[which(o_files == i)])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, bad_sd_Deaths_Normal_dim_0[which(bad_normal == i)])
    }
    if(temp[i,2] == "A"){
      total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, bad_sd_Deaths_AF_dim_0[which(bad_af == i)])
    }
    if(temp[i,2] == "~"){
      total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, bad_sd_Deaths_Rand_dim_0[which(bad_r == i)])
    }
    if(temp[i,2] == "O"){
      total_sd_deaths_dim0 <- append(total_sd_deaths_dim0, bad_sd_Deaths_O_dim_0[which(bad_o == i)])
    }  
}
}

################################ dim 1 ################################ 
total_means_births_dim1 <- c()
total_sd_births_dim1 <- c()
total_means_deaths_dim1 <- c()
total_sd_deaths_dim1 <- c()

#Store the birth 1 dimensional means.
for(i in seq(from = 2001, to = 4000)){
  if(i %in% normal_files){
    total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_Normal_dim_1[which(normal_files == i)])
  }
  if(i %in% af_files){
    total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_AF_dim_1[which(af_files == i)])
  }
  if(i %in% r_files){
    total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_Rand_dim_1[which(r_files == i)])
    print(i)
  }
  if(i %in% o_files){
    total_means_births_dim1 <- append(total_means_births_dim1, mean_Births_O_dim_1[which(o_files == i)])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_means_births_dim1 <- append(total_means_births_dim1, bad_mean_Births_Normal_dim_1[which(bad_normal == i)])
    }
    if(temp[i,2] == "A"){
      total_means_births_dim1 <- append(total_means_births_dim1, bad_mean_Births_AF_dim_1[which(bad_af == i)])
    }
    if(temp[i,2] == "~"){
      total_means_births_dim1 <- append(total_means_births_dim1, bad_mean_Births_Rand_dim_1[which(bad_r == i)])
    }
    if(temp[i,2] == "O"){
      total_means_births_dim1 <- append(total_means_births_dim1, bad_mean_Births_O_dim_1[which(bad_o == i)])
    }  
  }
}

#Store the birth 1 dimensional sd.
for(i in seq(from = 2001, to = 4000)){ 
  if(i %in% normal_files){
    total_sd_births_dim1 <- append(total_sd_births_dim1, sd_Births_Normal_dim_1[which(normal_files == i)])
  }
  if(i %in% af_files){
    total_sd_births_dim1 <- append(total_sd_births_dim1, mean_Births_AF_dim_1[which(af_files == i)])
  }
  if(i %in% r_files){
    total_sd_births_dim1 <- append(total_sd_births_dim1, mean_Births_Rand_dim_1[which(r_files == i)])
  }
  if(i %in% o_files){
    total_sd_births_dim1 <- append(total_sd_births_dim1, mean_Births_O_dim_1[which(o_files == i)])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_sd_births_dim1 <- append(total_sd_births_dim1, bad_sd_Births_Normal_dim_1[which(bad_normal == i)])
    }
    if(temp[i,2] == "A"){
      total_sd_births_dim1 <- append(total_sd_births_dim1, bad_sd_Births_AF_dim_1[which(bad_af == i)])
    }
    if(temp[i,2] == "~"){
      total_sd_births_dim1 <- append(total_sd_births_dim1, bad_sd_Births_Rand_dim_1[which(bad_r == i)])
    }
    if(temp[i,2] == "O"){
      total_sd_births_dim1 <- append(total_sd_births_dim1, bad_sd_Births_O_dim_1[which(bad_o == i)])
    }  
}
}

#Store the death 1 dimensional means.
for(i in seq(from = 2001, to = 4000)){
  if(i %in% normal_files){
    print("normal")
    total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_Normal_dim_1[which(normal_files == i)])
  }
  if(i %in% af_files){
    print("af")
    total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_AF_dim_1[which(af_files == i)])
  }
  if(i %in% r_files){
    print("rand")
    total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_Rand_dim_1[which(r_files == i)])
  }
  if(i %in% o_files){
    print("o")
    total_means_deaths_dim1 <- append(total_means_deaths_dim1, mean_Deaths_O_dim_1[which(o_files == i)])
  }
  if(i %in% pers_bad_index2){
    print(i)
    if(temp[i,2] == "N"){
      total_means_deaths_dim1 <- append(total_means_deaths_dim1, bad_mean_Deaths_Normal_dim_1[which(bad_normal == i)])
    }
    if(temp[i,2] == "A"){
      total_means_deaths_dim1 <- append(total_means_deaths_dim1, bad_mean_Deaths_AF_dim_1[which(bad_af == i)])
    }
    if(temp[i,2] == "~"){
      total_means_deaths_dim1 <- append(total_means_deaths_dim1, bad_mean_Deaths_Rand_dim_1[which(bad_r == i)])
    }
    if(temp[i,2] == "O"){
      total_means_deaths_dim1 <- append(total_means_deaths_dim1, bad_mean_Deaths_O_dim_1[which(bad_o == i)])
    }  
}
  
}

#Store the birth 1 dimensional sd.
for(i in seq(from = 2001, to = 4000)){ 
  if(i %in% normal_files){
    total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_Normal_dim_1[which(normal_files == i)])
  }
  if(i %in% af_files){
    total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_AF_dim_1[which(af_files == i)])
  }
  if(i %in% r_files){
    total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_Rand_dim_1[which(r_files == i)])
  }
  if(i %in% o_files){
    total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, sd_Deaths_O_dim_1[which(o_files == i)])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, bad_sd_Deaths_Normal_dim_1[which(bad_normal == i)])
    }
    if(temp[i,2] == "A"){
      total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, bad_sd_Deaths_AF_dim_1[which(bad_af == i)])
    }
    if(temp[i,2] == "~"){
      total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, bad_sd_Deaths_Rand_dim_1[which(bad_r == i)])
    }
    if(temp[i,2] == "O"){
      total_sd_deaths_dim1 <- append(total_sd_deaths_dim1, bad_sd_Deaths_O_dim_1[which(bad_o == i)])
    }  
}
}

################################ dim 2 ################################ 
total_means_births_dim2 <- c()
total_sd_births_dim2 <- c()

total_means_deaths_dim2 <- c()
total_sd_deaths_dim2 <- c()

#Store the birth 2 dimensional means.
for(i in seq(from = 2001, to = 4000)){
  if(i %in% normal_files){
    total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_Normal_dim_2[which(normal_files == i)])
  }
  if(i %in% af_files){
    total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_AF_dim_2[which(af_files == i)]) 
  }
  if(i %in% r_files){
    total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_Rand_dim_2[which(r_files == i)])
  }
  if(i %in% o_files){
    total_means_births_dim2 <- append(total_means_births_dim2, mean_Births_O_dim_2[which(o_files == i)])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_means_births_dim2 <- append(total_means_births_dim2, bad_mean_Births_Normal_dim_2[which(bad_normal == i)])
    }
    if(temp[i,2] == "A"){
      total_means_births_dim2 <- append(total_means_births_dim2, bad_mean_Births_AF_dim_2[which(bad_af == i)]) 
    }
    if(temp[i,2] == "~"){
      total_means_births_dim2 <- append(total_means_births_dim2, bad_mean_Births_Rand_dim_2[which(bad_r == i)])
    }
    if(temp[i,2] == "O"){
      total_means_births_dim2 <- append(total_means_births_dim2, bad_mean_Births_O_dim_2[which(bad_o == i)])
    }  
}
}

#Store the birth 2 dimesional sd.
for(i in seq(from = 2001, to = 4000)){ 
  if(i %in% normal_files){
    total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_Normal_dim_2[which(normal_files == i)])
  }
  if(i %in% af_files){
    total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_AF_dim_2[which(af_files == i)]) 
  }
  if(i %in% r_files){
    total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_Rand_dim_2[which(r_files == i)])
  }
  if(i %in% o_files){
    total_sd_births_dim2 <- append(total_sd_births_dim2, sd_Births_O_dim_2[which(o_files == i)])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_sd_births_dim2 <- append(total_sd_births_dim2, bad_sd_Births_Normal_dim_2[which(bad_normal == i)])
    }
    if(temp[i,2] == "A"){
      total_sd_births_dim2 <- append(total_sd_births_dim2, bad_sd_Births_AF_dim_2[which(bad_af == i)]) 
    }
    if(temp[i,2] == "~"){
      total_sd_births_dim2 <- append(total_sd_births_dim2, bad_sd_Births_Rand_dim_2[which(bad_r == i)])
    }
    if(temp[i,2] == "O"){
      total_sd_births_dim2 <- append(total_sd_births_dim2, bad_sd_Births_O_dim_2[which(bad_o == i)])
    }  
}
}

#Store the death 2 dimensional means
for(i in seq(from = 2001, to = 4000)){ 
  if(i %in% normal_files){
    total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_Normal_dim_2[which(normal_files == i)])
  }
  if(i %in% af_files){
    total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_AF_dim_2[which(af_files == i)])
  }
  if(i %in% r_files){
    total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_Rand_dim_2[which(r_files == i)])
  }
  if(i %in% o_files){
    total_means_deaths_dim2 <- append(total_means_deaths_dim2, mean_Deaths_O_dim_2[which(o_files == i)])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_means_deaths_dim2 <- append(total_means_deaths_dim2, bad_mean_Deaths_Normal_dim_2[which(bad_normal == i)])
    }
    if(temp[i,2] == "A"){
      total_means_deaths_dim2 <- append(total_means_deaths_dim2, bad_mean_Deaths_AF_dim_2[which(bad_af == i)])
    }
    if(temp[i,2] == "~"){
      total_means_deaths_dim2 <- append(total_means_deaths_dim2, bad_mean_Deaths_Rand_dim_2[which(bad_r == i)])
    }
    if(temp[i,2] == "O"){
      total_means_deaths_dim2 <- append(total_means_deaths_dim2, bad_mean_Deaths_O_dim_2[which(bad_o == i)])
    }  
}
}

#Store the death 2 dimensional sd.
for(i in seq(from = 2001, to = 4000)){  
  if(i %in% normal_files){
    total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_Normal_dim_2[which(normal_files == i)])
  }
  if(i %in% af_files){
    total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_AF_dim_2[which(af_files == i)])
  }
  if(i %in% r_files){
    total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_Rand_dim_2[which(r_files == i)])
  }
  if(i %in% o_files){
    total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, sd_Deaths_O_dim_2[which(o_files == i)])
  }
  if(i %in% pers_bad_index2){
    if(temp[i,2] == "N"){
      total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, bad_sd_Deaths_Normal_dim_2[which(bad_normal == i)])
    }
    if(temp[i,2] == "A"){
      total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, bad_sd_Deaths_AF_dim_2[which(bad_af == i)])
    }
    if(temp[i,2] == "~"){
      total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, bad_sd_Deaths_Rand_dim_2[which(bad_r == i)])
    }
    if(temp[i,2] == "O"){
      total_sd_deaths_dim2 <- append(total_sd_deaths_dim2, bad_sd_Deaths_O_dim_2[which(bad_o == i)])
    }  
}
}
```
##Organize mean, sd data into dataframe
```{r}
export_dim0 <- data.frame("Means_dim0_birth" = total_means_births_dim0, "Means_dim0_death" = total_means_deaths_dim0, "sd_dim0_birth" = total_sd_births_dim0, "sd_dim0_death" = total_sd_deaths_dim0)

export_dim1 <- data.frame("Means_dim1_birth" = total_means_births_dim1, "Means_dim1_death" = total_means_deaths_dim1, "sd_dim1_birth" = total_sd_births_dim1, "sd_dim1_death" = total_sd_deaths_dim1)
 
export_dim2 <- data.frame("Means_dim2_birth" = total_means_births_dim2, "Means_dim2_death" = total_means_deaths_dim2, "sd_dim2_birth" = total_sd_births_dim2, "sd_dim2_death" = total_sd_deaths_dim2)
```

```{r}
write.csv(export_dim0, "2001_4000_Organized_Mean_sd_dimension_0.csv") 
write.csv(export_dim1, "2001_4000_Organized_Mean_sd_dimension_1.csv") 
write.csv(export_dim2, "2001-4000_Organized_Mean_sd_dimension_2.csv")
```
