---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r}
temp <- as.matrix(read.csv("/Users/Luke/Desktop/github/TDA-MSRI-2018/200_set_of_Norm_AF_Rand.csv", header = T)) 
##DONT FORGET TO DELETE THE FIRST COLUMN!!! Not done here because it is already gone. 

directory <-"/Users/Luke/Desktop/github/TDA-MSRI-2018/Perstdiagram_reduction/"

for(i in seq(length(temp))){
  assign(paste0("persistence", i), as.matrix(read.csv(file = paste0(directory, "perstdiag ", temp[i], ".csv")), header = T)[,-1])
  }
```

```{r}
#Prints the number of 0, 1 and 2 dimensional features in a vector.
zeros<-0
ones<-0
twos<-0

Counting_Dimensions <- function(n) {
  tempFrame <- data.frame("Dimension" = get(paste0("persistence", n))[,1], "Birth" = get(paste0("persistence", n))[,2], get(paste0("persistence", n))[,3])  
  return(table(tempFrame$Dimension))
}
```

```{r}
#############################

compute_zeros_birth <- function(n,a){
  L <- c()
  for(i in seq(a)){
   L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
}

compute_zeros_death <- function(n,a){
  L <- c()
  for(i in seq(a)){
   L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
}
###############################  
compute_ones_birth <- function(n,a,b){
  L <- c()
  for(i in seq(from=a+1, to=a+b)){
   L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
}

compute_ones_death <- function(n,a,b){
  L <- c()
  for(i in seq(from=a+1, to=a+b)){
   L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
}
#################
compute_twos_birth <- function(n,a,b,c){
  L <- c()
  for(i in seq(from=a+b+1, to=a+b+c)){
  L <- append(L , get(paste0("persistence", n))[i,2])
  }
  return(L)
} 


compute_twos_death <- function(n,a,b,c){
  L <- c()
  for(i in seq(from=a+b+1, to=a+b+c)){
  L <- append(L , get(paste0("persistence", n))[i,3])
  }
  return(L)
} 
  
```

##Extacts birth, death times for each dimension
```{r}

Extract_Birth_Zeros <- function(n){ #n is desired dimension
    p <- c()
    a <- Counting_Dimensions(n)[1]
    #b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth variables.
    assign(paste0("pers_", n, "_zeros_birth"), compute_zeros_birth(n,a))
    p <- append(p, get(paste0("pers_", n, "_zeros_birth")))
    return(p)
}

Extract_Death_Zeros <- function(n){ #n is desired dimension
    p <- c()
    a <- Counting_Dimensions(n)[1]
    #b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables
    assign(paste0("pers_", n, "_zeros_death"), compute_zeros_death(n,a))
    p <- append(p, get(paste0("pers_", n, "_zeros_death")))
    return(p)
    # k <- 0
    # assign(k, compute_zeros_death(n,a))
    # return(k)
}

Extract_Birth_Ones <- function(n){ #n is desired dimension
    p<- c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables.
    assign(paste0("pers_", n, "_ones_birth"), compute_ones_birth(n,a,b)) 
    p <- append(p, get(paste0("pers_", n, "_ones_birth")))
    return(p)
}

Extract_Death_Ones <- function(n){ #n is desired dimension
    p<- c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    #c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables.
    assign(paste0("pers_", n, "_ones_death"), compute_ones_death(n,a,b)) 
    p <- append(p, get(paste0("pers_", n, "_ones_death")))
    return(p)
}

Extract_Birth_Twos <- function(n){ #n is desired dimension
    p<-c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    c <- Counting_Dimensions(n)[3]
    
    #Assigns birth variables.
    assign(paste0("pers_", n, "_twos_birth"), compute_twos_birth(n,a,b,c)) 
    p <- append(p, get(paste0("pers_", n, "_twos_birth")))
    return(p)    
}
Extract_Death_Twos <- function(n){ #n is desired dimension
    p<-c()
    a <- Counting_Dimensions(n)[1]
    b <- Counting_Dimensions(n)[2]
    c <- Counting_Dimensions(n)[3]
    
    #Assigns birth and death variables.
    assign(paste0("pers_", n, "_twos_death"), compute_twos_death(n,a,b,c)) 
    p <- append(p, get(paste0("pers_", n, "_twos_death")))
    return(p)    
}

```
##Systematically store all 1200 datasets

##THIS WILL PRODUCE A SHITTON OF VARIABLES IN YOUR GLOBAL ENVIRONMENT
```{r}
#Stores pers_zeros_births
for(i in seq(length(temp))){
   assign(paste0("pers_", i, "_zeros_birth"), Extract_Birth_Zeros(i),envir=.GlobalEnv)
}
#Stores pers_zeros_deaths
for(i in seq(length(temp))){
   assign(paste0("pers_", i, "_zeros_death"), Extract_Death_Zeros(i),envir=.GlobalEnv)
}
#Stores pers_ones_births
for(i in seq(length(temp))){
   assign(paste0("pers_", i, "_ones_birth"), Extract_Birth_Ones(i),envir=.GlobalEnv)
}
#Stores pers_ones_deaths
for(i in seq(length(temp))){
   assign(paste0("pers_", i, "_ones_death"), Extract_Death_Ones(i),envir=.GlobalEnv)
}
#Stores pers_twos_births
for(i in seq(length(temp))){
  print(i)
  assign(paste0("pers_", i, "_twos_birth"), Extract_Birth_Twos(i),envir=.GlobalEnv)
}
#Stores pers_twos_deaths
for(i in seq(length(temp))){
  print(i)
  assign(paste0("pers_", i, "_twos_death"), Extract_Death_Twos(i),envir=.GlobalEnv)
}
```

#Below is an alternative function that simply calculates and stored the distance values from the diagonal.
```{r}
Diag_Distances <- function(birth_pts, death_pts, thres){
  p <- c()
  for(i in seq(length(birth_pts))){
    x <- birth_pts[i]
    y <- death_pts[i]
    #print(i)
    d <- (abs(x-y)/sqrt(x^2 + y^2))
    if(is.na(d) == FALSE & d <= thres){
      p <- append(p, d)
    }
  }
  return(p)
}
```
#Store the different classes.
```{r}
#We'll put together 200 normals and store their averages across the first and second dimensions.
Births_Normal_dim_0 <- c()
Births_Normal_dim_1 <- c()
Births_Normal_dim_2 <- c()

for(i in seq(200)){
  Births_Normal_dim_0 <- append(Births_Normal_dim_0, get(paste0("pers_", i, "_zeros_birth")))
  
  Births_Normal_dim_1 <- append(Births_Normal_dim_1, get(paste0("pers_", i, "_ones_birth")))

  Births_Normal_dim_2 <- append(Births_Normal_dim_2,  get(paste0("pers_", i, "_twos_birth")))
}

Births_AF_dim_0 <- c()
Births_AF_dim_1 <- c()
Births_AF_dim_2 <- c()

for(i in seq(from = 200, to = 400)){
  Births_AF_dim_0 <- append(Births_AF_dim_0, get(paste0("pers_", i, "_zeros_birth")))
  
  Births_AF_dim_1 <- append(Births_AF_dim_1, get(paste0("pers_", i, "_ones_birth")))

  Births_AF_dim_2 <- append(Births_AF_dim_2,  get(paste0("pers_", i, "_twos_birth")))
}

Births_Rand_dim_0 <- c()
Births_Rand_dim_1 <- c()
Births_Rand_dim_2 <- c()

for(i in seq(from = 400, to = 600)){
  Births_Rand_dim_0 <- append(Births_Rand_dim_0, get(paste0("pers_", i, "_zeros_birth")))

  Births_Rand_dim_1 <- append(Births_Rand_dim_1, get(paste0("pers_", i, "_ones_birth")))

  Births_Rand_dim_2 <- append(Births_Rand_dim_2,  get(paste0("pers_", i, "_twos_birth")))
}

```
#Don't know if we need this code block below.
```{r}
#We'll put together 200 normals and store their averages across the first and second dimensions.
Deaths_Normal_dim_0 <- c()
Deaths_Normal_dim_1 <- c()
Deaths_Normal_dim_2 <- c()

for(i in seq(200)){
  Deaths_Normal_dim_0 <- append(Deaths_Normal_dim_0, get(paste0("pers_", i, "_zeros_death")))
  Deaths_Normal_dim_1 <- append(Deaths_Normal_dim_1, get(paste0("pers_", i, "_ones_death")))
  Deaths_Normal_dim_2 <- append(Deaths_Normal_dim_2,  get(paste0("pers_", i, "_twos_death")))
}

Deaths_AF_dim_0 <- c()
Deaths_AF_dim_1 <- c()
Deaths_AF_dim_2 <- c()

for(i in seq(from = 200, to = 400)){
  Deaths_AF_dim_0 <- append(Deaths_AF_dim_0, get(paste0("pers_", i, "_zeros_death")))
  Deaths_AF_dim_1 <- append(Deaths_AF_dim_1, get(paste0("pers_", i, "_ones_death")))
  Deaths_AF_dim_2 <- append(Deaths_AF_dim_2,  get(paste0("pers_", i, "_twos_death")))
}

Deaths_Rand_dim_0 <- c()
Deaths_Rand_dim_1 <- c()
Deaths_Rand_dim_2 <- c()

for(i in seq(from = 400, to = 600)){
  Deaths_Rand_dim_0 <- append(Deaths_Rand_dim_0, get(paste0("pers_", i, "_zeros_death")))
  Deaths_Rand_dim_1 <- append(Deaths_Rand_dim_1, get(paste0("pers_", i, "_ones_death")))
  Deaths_Rand_dim_2 <- append(Deaths_Rand_dim_2,  get(paste0("pers_", i, "_twos_death")))
}

```
#Evaluate how much shit we got 
```{r}
length(Births_Normal_dim_0)
length(Deaths_Normal_dim_0)
######
length(Births_AF_dim_0)
length(Deaths_AF_dim_0)
######
length(Births_Rand_dim_0)
length(Deaths_Rand_dim_0)
######
```

```{r}
#Normal, AF, then random
Mean_death_dim_0 <- Deaths_Normal_dim_0[1:(length(Deaths_Normal_dim_0)-1)] #Get rid of inf
```

#Store the averages, sd's.
```{r}
#We'll put together 200 normals and store their averages across the first and second dimensions.

mean_Births_Normal_dim_1 <- c()
mean_Births_Normal_dim_2 <- c()

sd_Births_Normal_dim_1 <- c()
sd_Births_Normal_dim_2 <- c()

for(i in seq(200)){
  mean_Births_Normal_dim_1 <- append(mean_Births_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

  mean_Births_Normal_dim_2 <- append(mean_Births_Normal_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_Normal_dim_1 <- append(sd_Births_Normal_dim_1, 0)
  }
  
  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_Normal_dim_2 <- append(sd_Births_Normal_dim_2, 0)
  }
}

mean_Births_AF_dim_1 <- c()
mean_Births_AF_dim_2 <- c()

sd_Births_AF_dim_1 <- c()
sd_Births_AF_dim_2 <- c()

for(i in seq(from = 201, to = 400)){
  mean_Births_AF_dim_1 <- append(mean_Births_AF_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

  mean_Births_AF_dim_2 <- append(mean_Births_AF_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))
  
  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_AF_dim_1 <- append(sd_Births_AF_dim_1, 0)
  }
  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_AF_dim_2 <- append(sd_Births_AF_dim_2, 0)
  }
}

mean_Births_Rand_dim_1 <- c()
mean_Births_Rand_dim_2 <- c()

sd_Births_Rand_dim_1 <- c()
sd_Births_Rand_dim_2 <- c()

for(i in seq(from = 401, to = 600)){
  mean_Births_Rand_dim_1 <- append(mean_Births_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_birth"))))

  mean_Births_Rand_dim_2 <- append(mean_Births_Rand_dim_2,  mean(get(paste0("pers_", i, "_twos_birth"))))

  if(length(get(paste0("pers_", i, "_ones_birth"))) != 1){
    sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_birth"))))
  }
  else{
    sd_Births_Rand_dim_1 <- append(sd_Births_Rand_dim_1, 0)
  }
  
  if(length(get(paste0("pers_", i, "_twos_birth"))) != 1){
    sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, sd(get(paste0("pers_", i, "_twos_birth"))))
  }
  else{
    sd_Births_Rand_dim_2 <- append(sd_Births_Rand_dim_2, 0)
  }
    
}

```
#Don't know if we need this code block below.
```{r}
#We'll put together 200 normals and store their averages across the first and second dimensions.
mean_Deaths_Normal_dim_0 <- c()
mean_Deaths_Normal_dim_1 <- c()
mean_Deaths_Normal_dim_2 <- c()

sd_Deaths_Normal_dim_0 <- c()
sd_Deaths_Normal_dim_1 <- c()
sd_Deaths_Normal_dim_2 <- c()

for(i in seq(200)){
  mean_Deaths_Normal_dim_0 <- append(mean_Deaths_Normal_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_Normal_dim_1 <- append(mean_Deaths_Normal_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_Normal_dim_2 <- append(mean_Deaths_Normal_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))
  
  if(length(get(paste0("pers_", i, "_zeros_death")) != 1)){
    sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_Normal_dim_0 <- append(sd_Deaths_Normal_dim_0, 0)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
    sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_Normal_dim_1 <- append(sd_Deaths_Normal_dim_1, 0)
  } 
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))
  }
  else{
    sd_Deaths_Normal_dim_2 <- append(sd_Deaths_Normal_dim_2, 0)
  }
}

mean_Deaths_AF_dim_0 <- c()
mean_Deaths_AF_dim_1 <- c()
mean_Deaths_AF_dim_2 <- c()

sd_Deaths_AF_dim_0 <- c()
sd_Deaths_AF_dim_1 <- c()
sd_Deaths_AF_dim_2 <- c()

for(i in seq(from = 201, to = 400)){
  mean_Deaths_AF_dim_0 <- append(mean_Deaths_AF_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_AF_dim_1 <- append(mean_Deaths_AF_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_AF_dim_2 <- append(mean_Deaths_AF_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))
  
  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){
    sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_AF_dim_0 <- append(sd_Deaths_AF_dim_0, 0)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){  
    sd_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    d_Deaths_AF_dim_1 <- append(sd_Deaths_AF_dim_1, 0)
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, sd(get(paste0("pers_", i, "_twos_death"))))  
  }
  else{
    sd_Deaths_AF_dim_2 <- append(sd_Deaths_AF_dim_2, 0)
  }
}  
  
mean_Deaths_Rand_dim_0 <- c()
mean_Deaths_Rand_dim_1 <- c()
mean_Deaths_Rand_dim_2 <- c()

sd_Deaths_Rand_dim_0 <- c()
sd_Deaths_Rand_dim_1 <- c()
sd_Deaths_Rand_dim_2 <- c()

for(i in seq(from = 401, to = 600)){
  mean_Deaths_Rand_dim_0 <- append(mean_Deaths_Rand_dim_0, mean(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  mean_Deaths_Rand_dim_1 <- append(mean_Deaths_Rand_dim_1, mean(get(paste0("pers_", i, "_ones_death"))))
  mean_Deaths_Rand_dim_2 <- append(mean_Deaths_Rand_dim_2, mean(get(paste0("pers_", i, "_twos_death"))))
  
  if(length(get(paste0("pers_", i, "_zeros_death"))) != 1){ 
    sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, sd(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)]))
  }
  else{
    sd_Deaths_Rand_dim_0 <- append(sd_Deaths_Rand_dim_0, 0)
  }
  if(length(get(paste0("pers_", i, "_ones_death"))) != 1){
  sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, sd(get(paste0("pers_", i, "_ones_death"))))
  }
  else{
    sd_Deaths_Rand_dim_1 <- append(sd_Deaths_Rand_dim_1, 0)    
  }
  if(length(get(paste0("pers_", i, "_twos_death"))) != 1){
    sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, sd(get(paste0("pers_", i, "_twos_death")))) 
  }
  else{
    sd_Deaths_Rand_dim_2 <- append(sd_Deaths_Rand_dim_2, 0)
  }
}

```

```{r}
#dim0, births
#Append the means, standard deviations. 
total_means_births_dim0 <-seq(0,0,length.out=600)

total_sd_births_dim0 <- seq(0,0,length.out=600)

#dim0, deaths
#Append the means, standard deviations
total_means_deaths_dim0 <- append(append(mean_Deaths_Normal_dim_0, mean_Deaths_AF_dim_0), mean_Deaths_Rand_dim_0)

total_sd_deaths_dim0 <- append(append(sd_Deaths_Normal_dim_0, sd_Deaths_AF_dim_0), sd_Deaths_Rand_dim_0)

###################################################################

#dim1, births
#Append the means, standard deviations. 
total_means_births_dim1 <- append(append(mean_Births_Normal_dim_1, mean_Births_AF_dim_1), mean_Births_Rand_dim_1)

total_sd_births_dim1 <- append(append(sd_Births_Normal_dim_1, sd_Births_AF_dim_1), sd_Births_Rand_dim_1)

#dim1, deaths
#Append the means, standard deviations
total_means_deaths_dim1 <- append(append(mean_Deaths_Normal_dim_1, mean_Deaths_AF_dim_1), mean_Deaths_Rand_dim_1)

total_sd_deaths_dim1 <- append(append(sd_Deaths_Normal_dim_1, sd_Deaths_AF_dim_1), sd_Deaths_Rand_dim_1)

###################################################################

#dim2, births
#Append the means, standard deviations. 
total_means_births_dim2 <- append(append(mean_Births_Normal_dim_2, mean_Births_AF_dim_2), mean_Births_Rand_dim_2)

total_sd_births_dim2 <- append(append(sd_Births_Normal_dim_2, sd_Births_AF_dim_2), sd_Births_Rand_dim_2)

#dim2, deaths
#Append the means, standard deviations
total_means_deaths_dim2 <- append(append(mean_Deaths_Normal_dim_2, mean_Deaths_AF_dim_2), mean_Deaths_Rand_dim_2)

total_sd_deaths_dim2 <- append(append(sd_Deaths_Normal_dim_2, sd_Deaths_AF_dim_2), sd_Deaths_Rand_dim_2)

```
##Organize data into dataframe, export into CSV.
```{r}
export_dim0 <- data.frame("Means_dim0_birth" = total_means_births_dim0, "Means_dim0_death" = total_means_deaths_dim0, "sd_dim0_birth" = total_sd_births_dim0, "sd_dim0_death" = total_sd_deaths_dim0)

export_dim1 <- data.frame("Means_dim1_birth" = total_means_births_dim1, "Means_dim1_death" = total_means_deaths_dim1, "sd_dim1_birth" = total_sd_births_dim1, "sd_dim1_death" = total_sd_deaths_dim1)

export_dim2 <- data.frame("Means_dim2_birth" = total_means_births_dim2, "Means_dim2_death" = total_means_deaths_dim2, "sd_dim2_birth" = total_sd_births_dim2, "sd_dim2_death" = total_sd_deaths_dim2)
```

```{r}
write.csv(export_dim0, "Reduced_Pers_Mean_sd_dimension_0.csv")
write.csv(export_dim1, "Reduced_Pers_Mean_sd_dimension_1.csv")
write.csv(export_dim2, "Reduced_Pers_Mean_sd_dimension_2.csv")
```
##Calculating total lifetimes. 
```{r}
#Lifetimes for dimension 0
lifetimes_dim0 <- c()
for(i in seq(length(temp))){
  lifetime <- sum(get(paste0("pers_", i, "_zeros_death"))[1:(length(get(paste0("pers_", i, "_zeros_death")))-1)])
  lifetimes_dim0 <- append(lifetimes_dim0, lifetime)
}

#Lifetimes for dimension 1.
lifetimes_dim1 <- c()
for(i in seq(length(temp))){
  lifetime <- sum(get(paste0("pers_", i, "_ones_death"))) - sum(get((paste0("pers_", i, "_ones_birth"))))
  lifetimes_dim1 <- append(lifetimes_dim1, lifetime)
}

#Lifetimes for dimension 2.
lifetimes_dim2 <- c()
for(i in seq(length(temp))){
  lifetime <- sum((get(paste0("pers_", i, "_twos_death")))) - sum(get((paste0("pers_", i, "_twos_birth"))))
  lifetimes_dim2 <- append(lifetimes_dim2, lifetime)
}
```
#Convert to dataframe, export as CSV. 
```{r}
lifetimedata <- data.frame("Lifetime_dim0" = lifetimes_dim0, "Lifetime_dim1" = lifetimes_dim1, "Lifetime_dim2" = lifetimes_dim2)
write.csv(lifetimedata, file = "Reduced_Pers_Lifetimes_dim_0_1_2.csv")
```

```{r}

```

